---
title: "Recovery_DRC"
author: "Emma M Pfortmiller"
date: "2025-02-28"
site: workflowr::wflow_site
output:
  workflowr::wflow_html:
    toc: true
    toc_depth: 2
    toc_float: true
    theme: journal
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This contains data from all three individuals used for this timecourse experiment
78-1, 75-1, 17-3 iPSCs
50,000 cells in 60 wells of 6x 96 well plates 
Treated with varying concentrations of doxrubicin, 5-fluorouracil, and DMSO vehicle matched controls

78-1 = Ind3
75-1 = Ind4
17-3 = Ind5

```{r Libraries, echo = FALSE}
library(tidyverse)
library(dplyr)
library(scales)
library(drc)
library(readxl)
```

Import Datasets

```{r Full Dataset All Individuals, results=FALSE}
AllData <- read_excel("C:/Users/emmap/OneDrive/Desktop/Ward Lab/Experiments/DXR Project/DRCs/5FUProj_DRCTime_78-1_75-1_17-3_EMP_240226.xlsx",
     sheet = "Fin_Sheet_Analysis")
View(AllData)

Ind3_78_data <- read_excel("C:/Users/emmap/OneDrive/Desktop/Ward Lab/Experiments/DXR Project/DRCs/5FUProj_DRCTime_78-1_75-1_17-3_EMP_240226.xlsx",
     sheet = "Fin_78_Sheet")
View(Ind3_78_data)

#this is actually ind 3 according to my RNAseq - 78-1 F

Ind4_75_data <- read_excel("C:/Users/emmap/OneDrive/Desktop/Ward Lab/Experiments/DXR Project/DRCs/5FUProj_DRCTime_78-1_75-1_17-3_EMP_240226.xlsx",
     sheet = "Fin_75_Sheet")
View(Ind4_75_data)

#this is actually ind 4 according to my RNAseq - 75-1 F

Ind5_17_data <- read_excel("C:/Users/emmap/OneDrive/Desktop/Ward Lab/Experiments/DXR Project/DRCs/5FUProj_DRCTime_78-1_75-1_17-3_EMP_240226.xlsx",
     sheet = "Fin_17_Sheet")
View(Ind5_17_data)

#this is actually ind 5 according to my RNAseq - 17-3 M

```

Now that I've imported my data, let's go ahead and filter the data to reflect time and treatment groups.
```{r Filter Data, echo=FALSE}
####all ind####
dox_all <- AllData %>% filter(Drug =="DOX")
dmso_all <- AllData %>% filter(Drug =="DMSO")

####Ind1 78-1####
dox_78 <- Ind3_78_data %>% filter(Drug=="DOX")
dmso_78 <- Ind3_78_data %>% filter(Drug=="DMSO")

####Ind4 75-1####
dox_75 <- Ind4_75_data %>% filter(Drug=="DOX")
dmso_75 <- Ind4_75_data %>% filter(Drug=="DMSO")

####Ind5 17-3####
dox_17 <- Ind5_17_data %>% filter(Drug=="DOX")
dmso_17 <- Ind5_17_data %>% filter(Drug=="DMSO")
```

```{r 5FU Data, include=FALSE}
# fluo_all <- AllData %>% filter(Drug =="FLUO")
# 
# fluo_75 <- Ind1_75_data %>% filter(Drug=="FLUO")
# 
# fluo_78 <- Ind2_78_data %>% filter(Drug=="FLUO")
# 
# fluo_17 <- Ind3_17_data %>% filter(Drug=="FLUO")

```

I have three timepoints that I'm investigating through this experiment, they will be treated separately
Let's filter the data accordingly by timepoint (24hr, 48hr, 72hr)
```{r Filter Data Timepoint, echo = FALSE}

####DOX Timepoints All####
dox24hrall <- dox_all %>% filter(FinTime == "24hr")
dox48hrall <- dox_all %>% filter(FinTime == "48hr")
dox72hrall <- dox_all %>% filter(FinTime == "72hr")


####DMSO Timepoints All####
dmso24hrall <- dmso_all %>% filter(FinTime == "24hr")
dmso48hrall <- dmso_all %>% filter(FinTime == "48hr")
dmso72hrall <- dmso_all %>% filter(FinTime == "72hr")

#Filter these again by individual

####DOX Timepoints 75-1####
dox24hr75 <- dox_75 %>% filter(FinTime == "24hr")
dox48hr75 <- dox_75 %>% filter(FinTime == "48hr")
dox72hr75 <- dox_75 %>% filter(FinTime == "72hr")

####DMSO Timepoints 75-1####
dmso24hr75 <- dmso_75 %>% filter(FinTime == "24hr")
dmso48hr75 <- dmso_75 %>% filter(FinTime == "48hr")
dmso72hr75 <- dmso_75 %>% filter(FinTime == "72hr")

####DOX Timepoints 78-1####
dox24hr78 <- dox_78 %>% filter(FinTime == "24hr")
dox48hr78 <- dox_78 %>% filter(FinTime == "48hr")
dox72hr78 <- dox_78 %>% filter(FinTime == "72hr")

####DMSO Timepoints 78-1####
dmso24hr78 <- dmso_78 %>% filter(FinTime == "24hr")
dmso48hr78 <- dmso_78 %>% filter(FinTime == "48hr")
dmso72hr78 <- dmso_78 %>% filter(FinTime == "72hr")

####DOX Timepoints 17-3####
dox24hr17 <- dox_17 %>% filter(FinTime == "24hr")
dox48hr17 <- dox_17 %>% filter(FinTime == "48hr")
dox72hr17 <- dox_17 %>% filter(FinTime == "72hr")

####DMSO Timepoints 17-3####
dmso24hr17 <- dmso_17 %>% filter(FinTime == "24hr")
dmso48hr17 <- dmso_17 %>% filter(FinTime == "48hr")
dmso72hr17 <- dmso_17 %>% filter(FinTime == "72hr")

```


```{r 5FU Filter Data, include=FALSE}

# ####FLUO Timepoints All####
# fluo24hrall <- fluo_all %>% filter(FinTime == "24hr")
# fluo48hrall <- fluo_all %>% filter(FinTime == "48hr")
# fluo72hrall <- fluo_all %>% filter(FinTime == "72hr")
# 
# ####FLUO Timepoints 75-1####
# fluo24hr75 <- fluo_75 %>% filter(FinTime == "24hr")
# fluo48hr75 <- fluo_75 %>% filter(FinTime == "48hr")
# fluo72hr75 <- fluo_75 %>% filter(FinTime == "72hr")
# 
# ####FLUO Timepoints 78-1####
# fluo24hr78 <- fluo_78 %>% filter(FinTime == "24hr")
# fluo48hr78 <- fluo_78 %>% filter(FinTime == "48hr")
# fluo72hr78 <- fluo_78 %>% filter(FinTime == "72hr")
# 
# ####FLUO Timepoints 17-3####
# fluo24hr17 <- fluo_17 %>% filter(FinTime == "24hr")
# fluo48hr17 <- fluo_17 %>% filter(FinTime == "48hr")
# fluo72hr17 <- fluo_17 %>% filter(FinTime == "72hr")

```


Now that these are filtered by individual, time, and drug - I will start plotting the data

First, I'll plot the 24hr timepoint raw data
```{r Boxplots Raw Data 24hr}

#####DOX Samples#####
#dox 78-1 24HR
par(mar = c(3.0, 3.0, 1.2, 1), mgp = c(2, .7, 0))
layout(matrix(c(1, 2, 1, 3), nrow = 2, ncol = 2), heights = c(0.5, 2, 2, 2))
#layout.show(3)
plot.new()
text(0.5,0.5,"RFLU by Concentration DOX - 78-1 24hr",cex = 2,font = 2)

boxplot(dox24hr78$Ind2_78_In ~ dox24hr78$Conc, 
        ylim = c(0, 80000), 
        ylab = "Cell Viability (RFLU)", 
        xlab = "Concentration (uM)", 
        main = "DOXORUBICIN 0hr 78-1 Raw Data"
)

boxplot(dox24hr78$Ind2_78_Fin ~ dox24hr78$Conc, 
        ylim = c(0,80000), 
        ylab = "Cell Viability (RFLU)", 
        xlab = "Concentration (uM)", 
        main = "DOXORUBICIN 24hr 78-1 Raw Data"
)

#dox 75-1 24HR
par(mar = c(3.0, 3.0, 1.2, 1), mgp = c(2, .7, 0))
layout(matrix(c(1, 2, 1, 3), nrow = 2, ncol = 2), heights = c(0.5, 2, 2, 2))
#layout.show(3)
plot.new()
text(0.5,0.5,"RFLU by Concentration DOX - 75-1 24hr",cex = 2,font = 2)

boxplot(dox24hr75$Ind1_75_In ~ dox24hr75$Conc, 
        ylim = c(0, 80000), 
        ylab = "Cell Viability (RFLU)", 
        xlab = "Concentration (uM)", 
        main = "DOXORUBICIN 0hr 75-1 Raw Data"
)

boxplot(dox24hr75$Ind1_75_Fin ~ dox24hr75$Conc, 
        ylim = c(0,80000), 
        ylab = "Cell Viability (RFLU)", 
        xlab = "Concentration (uM)", 
        main = "DOXORUBICIN 24hr 75-1 Raw Data"
)

#dox 17-3 24HR
par(mar = c(3.0, 3.0, 1.2, 1), mgp = c(2, .7, 0))
layout(matrix(c(1, 2, 1, 3), nrow = 2, ncol = 2), heights = c(0.5, 2, 2, 2))
#layout.show(3)
plot.new()
text(0.5,0.5,"RFLU by Concentration DOX - 17-3 24hr",cex = 2,font = 2)

boxplot(dox24hr17$Ind3_17_In ~ dox24hr17$Conc, 
        ylim = c(0, 80000), 
        ylab = "Cell Viability (RFLU)", 
        xlab = "Concentration (uM)", 
        main = "DOXORUBICIN 0hr 17-3 Raw Data"
)

boxplot(dox24hr17$Ind3_17_Fin ~ dox24hr17$Conc, 
        ylim = c(0,80000), 
        ylab = "Cell Viability (RFLU)", 
        xlab = "Concentration (uM)", 
        main = "DOXORUBICIN 24hr 17-3 Raw Data"
)

#####DMSO samples#####
#DMSO 78-1 24HR
par(mar = c(3.0, 3.0, 1.2, 1), mgp = c(2, .7, 0))
layout(matrix(c(1, 2, 1, 3), nrow = 2, ncol = 2), heights = c(0.5, 2, 2, 2))
#layout.show(3)
plot.new()
text(0.5,0.5,"RFLU by Concentration DMSO - 78-1 24hr",cex = 2,font = 2)

boxplot(dmso24hr78$Ind2_78_In ~ dmso24hr78$Conc, 
        ylim = c(0, 80000), 
        ylab = "Cell Viability (RFLU)", 
        xlab = "Concentration (uM)", 
        main = "DMSO VEHICLE 0hr 78-1"
)

boxplot(dmso24hr78$Ind2_78_Fin ~ dmso24hr78$Conc, 
        ylim = c(0,80000), 
        ylab = "Cell Viability (RFLU)", 
        xlab = "Concentration (uM)", 
        main = "DMSO VEHICLE 24hr 78-1"
)

#DMSO 75-1 24HR
par(mar = c(3.0, 3.0, 1.2, 1), mgp = c(2, .7, 0))
layout(matrix(c(1, 2, 1, 3), nrow = 2, ncol = 2), heights = c(0.5, 2, 2, 2))
#layout.show(3)
plot.new()
text(0.5,0.5,"RFLU by Concentration DMSO - 75-1 24hr",cex = 2,font = 2)

boxplot(dmso24hr75$Ind1_75_In ~ dmso24hr75$Conc, 
        ylim = c(0, 80000), 
        ylab = "Cell Viability (RFLU)", 
        xlab = "Concentration (uM)", 
        main = "DMSO VEHICLE 0hr 75-1"
)

boxplot(dmso24hr75$Ind1_75_Fin ~ dmso24hr75$Conc, 
        ylim = c(0,80000), 
        ylab = "Cell Viability (RFLU)", 
        xlab = "Concentration (uM)", 
        main = "DMSO VEHICLE 24hr 75-1"
)

#DMSO 17-3 24HR
par(mar = c(3.0, 3.0, 1.2, 1), mgp = c(2, .7, 0))
layout(matrix(c(1, 2, 1, 3), nrow = 2, ncol = 2), heights = c(0.5, 2, 2, 2))
#layout.show(3)
plot.new()
text(0.5,0.5,"RFLU by Concentration DMSO - 17-3 24hr",cex = 2,font = 2)

boxplot(dmso24hr17$Ind3_17_In ~ dmso24hr17$Conc, 
        ylim = c(0, 80000), 
        ylab = "Cell Viability (RFLU)", 
        xlab = "Concentration (uM)", 
        main = "DMSO VEHICLE 0hr 17-3"
)

boxplot(dmso24hr17$Ind3_17_Fin ~ dmso24hr17$Conc, 
        ylim = c(0,80000), 
        ylab = "Cell Viability (RFLU)", 
        xlab = "Concentration (uM)", 
        main = "DMSO VEHICLE 24hr 17-3"
)

```

```{r 5FU Raw Data 24hr, include=FALSE}
# #####FLUO samples#####
# #FLUO 78-1 24HR
# par(mar = c(3.0, 3.0, 1.2, 1), mgp = c(2, .7, 0))
# layout(matrix(c(1, 2, 1, 3), nrow = 2, ncol = 2), heights = c(0.5, 2, 2, 2))
# #layout.show(3)
# plot.new()
# text(0.5,0.5,"RFLU by Concentration FLUO - 78-1 24hr",cex = 2,font = 2)
# 
# boxplot(fluo24hr78$Ind2_78_In ~ fluo24hr78$Conc, 
#         ylim = c(0, 80000), 
#         ylab = "Cell Viability (RFLU)", 
#         xlab = "Concentration (uM)", 
#         main = "5-FLUOROURACIL 0hr 78-1"
# )
# 
# boxplot(fluo24hr78$Ind2_78_Fin ~ fluo24hr78$Conc, 
#         ylim = c(0,80000), 
#         ylab = "Cell Viability (RFLU)", 
#         xlab = "Concentration (uM)", 
#         main = "5-FLUOROURACIL 24hr 78-1"
# )
# 
# #FLUO 75-1 24HR
# par(mar = c(3.0, 3.0, 1.2, 1), mgp = c(2, .7, 0))
# layout(matrix(c(1, 2, 1, 3), nrow = 2, ncol = 2), heights = c(0.5, 2, 2, 2))
# #layout.show(3)
# plot.new()
# text(0.5,0.5,"RFLU by Concentration FLUO - 75-1 24hr",cex = 2,font = 2)
# 
# boxplot(fluo24hr75$Ind1_75_In ~ fluo24hr75$Conc, 
#         ylim = c(0, 80000), 
#         ylab = "Cell Viability (RFLU)", 
#         xlab = "Concentration (uM)", 
#         main = "5-FLUOROURACIL 0hr 75-1"
# )
# 
# boxplot(fluo24hr75$Ind1_75_Fin ~ fluo24hr75$Conc, 
#         ylim = c(0,80000), 
#         ylab = "Cell Viability (RFLU)", 
#         xlab = "Concentration (uM)", 
#         main = "5-FLUOROURACIL 24hr 75-1"
# )
# 
# #FLUO 17-3 24HR
# par(mar = c(3.0, 3.0, 1.2, 1), mgp = c(2, .7, 0))
# layout(matrix(c(1, 2, 1, 3), nrow = 2, ncol = 2), heights = c(0.5, 2, 2, 2))
# #layout.show(3)
# plot.new()
# text(0.5,0.5,"RFLU by Concentration FLUO - 17-3 24hr",cex = 2,font = 2)
# 
# boxplot(fluo24hr17$Ind3_17_In ~ fluo24hr17$Conc, 
#         ylim = c(0, 80000), 
#         ylab = "Cell Viability (RFLU)", 
#         xlab = "Concentration (uM)", 
#         main = "5-FLUOROURACIL 0hr 17-3"
# )
# 
# boxplot(fluo24hr17$Ind3_17_Fin ~ fluo24hr17$Conc, 
#         ylim = c(0, 80000), 
#         ylab = "Cell Viability (RFLU)", 
#         xlab = "Concentration (uM)", 
#         main = "5-FLUOROURACIL 24hr 17-3"
# )
```


Now let's look at the raw data for the 48hr timepoint
```{r Boxplots Raw Data 48hr}

#####DOX Samples#####
#DOX 78-1 48HR
par(mar = c(3.0, 3.0, 1.2, 1), mgp = c(2, .7, 0))
layout(matrix(c(1, 2, 1, 3), nrow = 2, ncol = 2), heights = c(0.5, 2, 2, 2))
#layout.show(3)
plot.new()
text(0.5,0.5,"RFLU by Concentration DOX - 78-1 48hr",cex = 2,font = 2)

boxplot(dox48hr78$Ind2_78_In ~ dox48hr78$Conc, 
        ylim = c(0, 80000), 
        ylab = "Cell Viability (RFLU)", 
        xlab = "Concentration (uM)", 
        main = "DOXORUBICIN 0hr 78-1"
)

boxplot(dox48hr78$Ind2_78_Fin ~ dox48hr78$Conc, 
        ylim = c(0,80000), 
        ylab = "Cell Viability (RFLU)", 
        xlab = "Concentration (uM)", 
        main = "DOXORUBICIN 48hr 78-1"
)

#DOXO 75-1 48HR
par(mar = c(3.0, 3.0, 1.2, 1), mgp = c(2, .7, 0))
layout(matrix(c(1, 2, 1, 3), nrow = 2, ncol = 2), heights = c(0.5, 2, 2, 2))
#layout.show(3)
plot.new()
text(0.5,0.5,"RFLU by Concentration DOX - 75-1 48hr",cex = 2,font = 2)

boxplot(dox48hr75$Ind1_75_In ~ dox48hr75$Conc, 
        ylim = c(0, 80000), 
        ylab = "Cell Viability (RFLU)", 
        xlab = "Concentration (uM)", 
        main = "DOXORUBICIN 0hr 75-1"
)

boxplot(dox48hr75$Ind1_75_Fin ~ dox48hr75$Conc, 
        ylim = c(0,80000), 
        ylab = "Cell Viability (RFLU)", 
        xlab = "Concentration (uM)", 
        main = "DOXORUBICIN 48hr 75-1"
)

#DOX 17-3 48HR
par(mar = c(3.0, 3.0, 1.2, 1), mgp = c(2, .7, 0))
layout(matrix(c(1, 2, 1, 3), nrow = 2, ncol = 2), heights = c(0.5, 2, 2, 2))
#layout.show(3)
plot.new()
text(0.5,0.5,"RFLU by Concentration DOX - 17-3 48hr",cex = 2,font = 2)

boxplot(dox48hr17$Ind3_17_In ~ dox48hr17$Conc, 
        ylim = c(0, 80000), 
        ylab = "Cell Viability (RFLU)", 
        xlab = "Concentration (uM)", 
        main = "DOXORUBICIN 0hr 17-3"
)

boxplot(dox48hr17$Ind3_17_Fin ~ dox48hr17$Conc, 
        ylim = c(0,80000), 
        ylab = "Cell Viability (RFLU)", 
        xlab = "Concentration (uM)", 
        main = "DOXORUBICIN 48hr 17-3"
)

#####DMSO samples#####
#DMSO 78-1 48HR
par(mar = c(3.0, 3.0, 1.2, 1), mgp = c(2, .7, 0))
layout(matrix(c(1, 2, 1, 3), nrow = 2, ncol = 2), heights = c(0.5, 2, 2, 2))
#layout.show(3)
plot.new()
text(0.5,0.5,"RFLU by Concentration DMSO - 78-1 48hr",cex = 2,font = 2)

boxplot(dmso48hr78$Ind2_78_In ~ dmso48hr78$Conc, 
        ylim = c(0, 80000), 
        ylab = "Cell Viability (RFLU)", 
        xlab = "Concentration (uM)", 
        main = "DMSO VEHICLE 0hr 78-1"
)

boxplot(dmso48hr78$Ind2_78_Fin ~ dmso48hr78$Conc, 
        ylim = c(0,80000), 
        ylab = "Cell Viability (RFLU)", 
        xlab = "Concentration (uM)", 
        main = "DMSO VEHICLE 48hr 78-1"
)

#DMSO 75-1 48HR
par(mar = c(3.0, 3.0, 1.2, 1), mgp = c(2, .7, 0))
layout(matrix(c(1, 2, 1, 3), nrow = 2, ncol = 2), heights = c(0.5, 2, 2, 2))
#layout.show(3)
plot.new()
text(0.5,0.5,"RFLU by Concentration DMSO - 75-1 48hr",cex = 2,font = 2)

boxplot(dmso48hr75$Ind1_75_In ~ dmso48hr75$Conc, 
        ylim = c(0, 80000), 
        ylab = "Cell Viability (RFLU)", 
        xlab = "Concentration (uM)", 
        main = "DMSO VEHICLE 0hr 75-1"
)

boxplot(dmso48hr75$Ind1_75_Fin ~ dmso48hr75$Conc, 
        ylim = c(0,80000), 
        ylab = "Cell Viability (RFLU)", 
        xlab = "Concentration (uM)", 
        main = "DMSO VEHICLE 48hr 75-1"
)

#DMSO 17-3 48HR
par(mar = c(3.0, 3.0, 1.2, 1), mgp = c(2, .7, 0))
layout(matrix(c(1, 2, 1, 3), nrow = 2, ncol = 2), heights = c(0.5, 2, 2, 2))
#layout.show(3)
plot.new()
text(0.5,0.5,"RFLU by Concentration DMSO - 17-3 48hr",cex = 2,font = 2)

boxplot(dmso48hr17$Ind3_17_In ~ dmso48hr17$Conc, 
        ylim = c(0, 80000), 
        ylab = "Cell Viability (RFLU)", 
        xlab = "Concentration (uM)", 
        main = "DMSO VEHICLE 0hr 17-3"
)

boxplot(dmso48hr17$Ind3_17_Fin ~ dmso48hr17$Conc, 
        ylim = c(0,80000), 
        ylab = "Cell Viability (RFLU)", 
        xlab = "Concentration (uM)", 
        main = "DMSO VEHICLE 48hr 17-3"
)


```

```{r 5FU Raw Samples 48hr, include=FALSE}
# #####FLUO samples#####
# #FLUO 78-1 48HR
# par(mar = c(3.0, 3.0, 1.2, 1), mgp = c(2, .7, 0))
# layout(matrix(c(1, 2, 1, 3), nrow = 2, ncol = 2), heights = c(0.5, 2, 2, 2))
# #layout.show(3)
# plot.new()
# text(0.5,0.5,"RFLU by Concentration FLUO - 78-1 48hr",cex = 2,font = 2)
# 
# boxplot(fluo48hr78$Ind2_78_In ~ fluo48hr78$Conc, 
#         ylim = c(0, 80000), 
#         ylab = "Cell Viability (RFLU)", 
#         xlab = "Concentration (uM)", 
#         main = "5-FLUOROURACIL 0hr 78-1"
# )
# 
# boxplot(fluo48hr78$Ind2_78_Fin ~ fluo48hr78$Conc, 
#         ylim = c(0,80000), 
#         ylab = "Cell Viability (RFLU)", 
#         xlab = "Concentration (uM)", 
#         main = "5-FLUOROURACIL 48hr 78-1"
# )
# 
# #FLUO 75-1 48HR
# par(mar = c(3.0, 3.0, 1.2, 1), mgp = c(2, .7, 0))
# layout(matrix(c(1, 2, 1, 3), nrow = 2, ncol = 2), heights = c(0.5, 2, 2, 2))
# #layout.show(3)
# plot.new()
# text(0.5,0.5,"RFLU by Concentration FLUO - 75-1 48hr",cex = 2,font = 2)
# 
# boxplot(fluo48hr75$Ind1_75_In ~ fluo48hr75$Conc, 
#         ylim = c(0, 80000), 
#         ylab = "Cell Viability (RFLU)", 
#         xlab = "Concentration (uM)", 
#         main = "5-FLUOROURACIL 0hr 75-1"
# )
# 
# boxplot(fluo48hr75$Ind1_75_Fin ~ fluo48hr75$Conc, 
#         ylim = c(0,80000), 
#         ylab = "Cell Viability (RFLU)", 
#         xlab = "Concentration (uM)", 
#         main = "5-FLUOROURACIL 48hr 75-1"
# )
# 
# #FLUO 17-3 48HR
# par(mar = c(3.0, 3.0, 1.2, 1), mgp = c(2, .7, 0))
# layout(matrix(c(1, 2, 1, 3), nrow = 2, ncol = 2), heights = c(0.5, 2, 2, 2))
# #layout.show(3)
# plot.new()
# text(0.5,0.5,"RFLU by Concentration FLUO - 17-3 48hr",cex = 2,font = 2)
# 
# boxplot(fluo48hr17$Ind3_17_In ~ fluo48hr17$Conc, 
#         ylim = c(0, 80000), 
#         ylab = "Cell Viability (RFLU)", 
#         xlab = "Concentration (uM)", 
#         main = "5-FLUOROURACIL 0hr 17-3"
# )
# 
# boxplot(fluo48hr17$Ind3_17_Fin ~ fluo48hr17$Conc, 
#         ylim = c(0, 80000), 
#         ylab = "Cell Viability (RFLU)", 
#         xlab = "Concentration (uM)", 
#         main = "5-FLUOROURACIL 48hr 17-3"
# )
```


```{r Boxplots Raw Data 72hr}

#####DOX Samples#####
#DOX 78-1 72HR
par(mar = c(3.0, 3.0, 1.2, 1), mgp = c(2, .7, 0))
layout(matrix(c(1, 2, 1, 3), nrow = 2, ncol = 2), heights = c(0.5, 2, 2, 2))
#layout.show(3)
plot.new()
text(0.5,0.5,"RFLU by Concentration DOX - 78-1 72hr",cex = 2,font = 2)

boxplot(dox72hr78$Ind2_78_In ~ dox72hr78$Conc, 
        ylim = c(0, 80000), 
        ylab = "Cell Viability (RFLU)", 
        xlab = "Concentration (uM)", 
        main = "DOXORUBICIN 0hr 78-1"
)

boxplot(dox72hr78$Ind2_78_Fin ~ dox72hr78$Conc, 
        ylim = c(0,80000), 
        ylab = "Cell Viability (RFLU)", 
        xlab = "Concentration (uM)", 
        main = "DOXORUBICIN 72hr 78-1"
)

#DOX 75-1 72HR
par(mar = c(3.0, 3.0, 1.2, 1), mgp = c(2, .7, 0))
layout(matrix(c(1, 2, 1, 3), nrow = 2, ncol = 2), heights = c(0.5, 2, 2, 2))
#layout.show(3)
plot.new()
text(0.5,0.5,"RFLU by Concentration DOX - 75-1 72hr",cex = 2,font = 2)

boxplot(dox72hr75$Ind1_75_In ~ dox72hr75$Conc, 
        ylim = c(0, 80000), 
        ylab = "Cell Viability (RFLU)", 
        xlab = "Concentration (uM)", 
        main = "DOXORUBICIN 0hr 75-1"
)

boxplot(dox72hr75$Ind1_75_Fin ~ dox72hr75$Conc, 
        ylim = c(0,80000), 
        ylab = "Cell Viability (RFLU)", 
        xlab = "Concentration (uM)", 
        main = "DOXORUBICIN 72hr 75-1"
)

#DOX 17-3 72HR
par(mar = c(3.0, 3.0, 1.2, 1), mgp = c(2, .7, 0))
layout(matrix(c(1, 2, 1, 3), nrow = 2, ncol = 2), heights = c(0.5, 2, 2, 2))
#layout.show(3)
plot.new()
text(0.5,0.5,"RFLU by Concentration DOX - 17-3 72hr",cex = 2,font = 2)

boxplot(dox72hr17$Ind3_17_In ~ dox72hr17$Conc, 
        ylim = c(0, 80000), 
        ylab = "Cell Viability (RFLU)", 
        xlab = "Concentration (uM)", 
        main = "DOXORUBICIN 0hr 17-3"
)

boxplot(dox72hr17$Ind3_17_Fin ~ dox72hr17$Conc, 
        ylim = c(0,80000), 
        ylab = "Cell Viability (RFLU)", 
        xlab = "Concentration (uM)", 
        main = "DOXORUBICIN 72hr 17-3"
)

#####DMSO samples#####
#DMSO 78-1 72HR
par(mar = c(3.0, 3.0, 1.2, 1), mgp = c(2, .7, 0))
layout(matrix(c(1, 2, 1, 3), nrow = 2, ncol = 2), heights = c(0.5, 2, 2, 2))
#layout.show(3)
plot.new()
text(0.5,0.5,"RFLU by Concentration DMSO - 78-1 72hr",cex = 2,font = 2)

boxplot(dmso72hr78$Ind2_78_In ~ dmso72hr78$Conc, 
        ylim = c(0, 80000), 
        ylab = "Cell Viability (RFLU)", 
        xlab = "Concentration (uM)", 
        main = "DMSO VEHICLE 0hr 78-1"
)

boxplot(dmso72hr78$Ind2_78_Fin ~ dmso72hr78$Conc, 
        ylim = c(0,80000), 
        ylab = "Cell Viability (RFLU)", 
        xlab = "Concentration (uM)", 
        main = "DMSO VEHICLE 72hr 78-1"
)

#DMSO 75-1 72HR
par(mar = c(3.0, 3.0, 1.2, 1), mgp = c(2, .7, 0))
layout(matrix(c(1, 2, 1, 3), nrow = 2, ncol = 2), heights = c(0.5, 2, 2, 2))
#layout.show(3)
plot.new()
text(0.5,0.5,"RFLU by Concentration DMSO - 75-1 72hr",cex = 2,font = 2)

boxplot(dmso72hr75$Ind1_75_In ~ dmso72hr75$Conc, 
        ylim = c(0, 80000), 
        ylab = "Cell Viability (RFLU)", 
        xlab = "Concentration (uM)", 
        main = "DMSO VEHICLE 0hr 75-1"
)

boxplot(dmso72hr75$Ind1_75_Fin ~ dmso72hr75$Conc, 
        ylim = c(0,80000), 
        ylab = "Cell Viability (RFLU)", 
        xlab = "Concentration (uM)", 
        main = "DMSO VEHICLE 72hr 75-1"
)

#DMSO 17-3 72HR
par(mar = c(3.0, 3.0, 1.2, 1), mgp = c(2, .7, 0))
layout(matrix(c(1, 2, 1, 3), nrow = 2, ncol = 2), heights = c(0.5, 2, 2, 2))
#layout.show(3)
plot.new()
text(0.5,0.5,"RFLU by Concentration DMSO - 17-3 72hr",cex = 2,font = 2)

boxplot(dmso72hr17$Ind3_17_In ~ dmso72hr17$Conc, 
        ylim = c(0, 80000), 
        ylab = "Cell Viability (RFLU)", 
        xlab = "Concentration (uM)", 
        main = "DMSO VEHICLE 0hr 17-3"
)

boxplot(dmso72hr17$Ind3_17_Fin ~ dmso72hr17$Conc, 
        ylim = c(0,80000), 
        ylab = "Cell Viability (RFLU)", 
        xlab = "Concentration (uM)", 
        main = "DMSO VEHICLE 72hr 17-3"
)
```


```{r 5FU Raw Data 72hr, include=FALSE}
# #####FLUO samples#####
# #FLUO 78-1 72HR
# par(mar = c(3.0, 3.0, 1.2, 1), mgp = c(2, .7, 0))
# layout(matrix(c(1, 2, 1, 3), nrow = 2, ncol = 2), heights = c(0.5, 2, 2, 2))
# #layout.show(3)
# plot.new()
# text(0.5,0.5,"RFLU by Concentration FLUO - 78-1 72hr",cex = 2,font = 2)
# 
# boxplot(fluo72hr78$Ind2_78_In ~ fluo72hr78$Conc, 
#         ylim = c(0, 80000), 
#         ylab = "Cell Viability (RFLU)", 
#         xlab = "Concentration (uM)", 
#         main = "5-FLUOROURACIL 0hr 78-1"
# )
# 
# boxplot(fluo72hr78$Ind2_78_Fin ~ fluo72hr78$Conc, 
#         ylim = c(0,80000), 
#         ylab = "Cell Viability (RFLU)", 
#         xlab = "Concentration (uM)", 
#         main = "5-FLUOROURACIL 72hr 78-1"
# )
# 
# #FLUO 75-1 72HR
# par(mar = c(3.0, 3.0, 1.2, 1), mgp = c(2, .7, 0))
# layout(matrix(c(1, 2, 1, 3), nrow = 2, ncol = 2), heights = c(0.5, 2, 2, 2))
# #layout.show(3)
# plot.new()
# text(0.5,0.5,"RFLU by Concentration FLUO - 75-1 72hr",cex = 2,font = 2)
# 
# boxplot(fluo72hr75$Ind1_75_In ~ fluo72hr75$Conc, 
#         ylim = c(0, 80000), 
#         ylab = "Cell Viability (RFLU)", 
#         xlab = "Concentration (uM)", 
#         main = "5-FLUOROURACIL 0hr 75-1"
# )
# 
# boxplot(fluo72hr75$Ind1_75_Fin ~ fluo72hr75$Conc, 
#         ylim = c(0,80000), 
#         ylab = "Cell Viability (RFLU)", 
#         xlab = "Concentration (uM)", 
#         main = "5-FLUOROURACIL 72hr 75-1"
# )
# 
# #FLUO 17-3 72HR
# par(mar = c(3.0, 3.0, 1.2, 1), mgp = c(2, .7, 0))
# layout(matrix(c(1, 2, 1, 3), nrow = 2, ncol = 2), heights = c(0.5, 2, 2, 2))
# #layout.show(3)
# plot.new()
# text(0.5,0.5,"RFLU by Concentration FLUO - 17-3 72hr",cex = 2,font = 2)
# 
# boxplot(fluo72hr17$Ind3_17_In ~ fluo72hr17$Conc, 
#         ylim = c(0, 80000), 
#         ylab = "Cell Viability (RFLU)", 
#         xlab = "Concentration (uM)", 
#         main = "5-FLUOROURACIL 0hr 17-3"
# )
# 
# boxplot(fluo72hr17$Ind3_17_Fin ~ fluo72hr17$Conc, 
#         ylim = c(0, 80000), 
#         ylab = "Cell Viability (RFLU)", 
#         xlab = "Concentration (uM)", 
#         main = "5-FLUOROURACIL 72hr 17-3"
# )

```


Now that I've taken a look at the raw data, let's look at the analyzed data step by step
The following steps were taken in analysis:
1. Import raw fluorescence values (RFLU) from platereader, baseline 0hr and final timepoints
2. Subtract background wells (prestoblue only wells) by plate
3. Subtract average of empty wells (galactose only, with 50k cells/well) by plate
4. Divide all values by matched vehicle average (ie DOX 0.01 / DMSO 0.01)
5. Divide initial 0hr value from final timepoint (24, 48, 72) value 
```{r Boxplots BG removed 24hr}
#####DOX Samples#####
#dox 78-1 no BG 24HR
par(mar = c(3.0, 3.0, 1.2, 1), mgp = c(2, .7, 0))
layout(matrix(c(1, 2, 1, 3), nrow = 2, ncol = 2), heights = c(0.5, 2, 2, 2))
#layout.show(3)
plot.new()
text(0.5,0.5,"DOX no BG - 78-1 24hr",cex = 2,font = 2)

boxplot(dox24hr78$Ind2_78_In_noBG ~ dox24hr78$Conc, 
        ylim = c(0, 80000), 
        ylab = "Cell Viability (RFLU)", 
        xlab = "Concentration (uM)", 
        main = "DOXORUBICIN 0hr 78-1 no BG"
)

boxplot(dox24hr78$Ind2_78_Fin_noBG ~ dox24hr78$Conc, 
        ylim = c(0,80000), 
        ylab = "Cell Viability (RFLU)", 
        xlab = "Concentration (uM)", 
        main = "DOXORUBICIN 24hr 78-1 no BG"
)

#dox 75-1 24HR
par(mar = c(3.0, 3.0, 1.2, 1), mgp = c(2, .7, 0))
layout(matrix(c(1, 2, 1, 3), nrow = 2, ncol = 2), heights = c(0.5, 2, 2, 2))
#layout.show(3)
plot.new()
text(0.5,0.5,"DOX no BG - 75-1 24hr",cex = 2,font = 2)

boxplot(dox24hr75$Ind1_75_In_noBG ~ dox24hr75$Conc, 
        ylim = c(0, 80000), 
        ylab = "Cell Viability (RFLU)", 
        xlab = "Concentration (uM)", 
        main = "DOXORUBICIN 0hr 75-1 no BG"
)

boxplot(dox24hr75$Ind1_75_Fin_noBG ~ dox24hr75$Conc, 
        ylim = c(0,80000), 
        ylab = "Cell Viability (RFLU)", 
        xlab = "Concentration (uM)", 
        main = "DOXORUBICIN 24hr 75-1 no BG"
)

#dox 17-3 24HR
par(mar = c(3.0, 3.0, 1.2, 1), mgp = c(2, .7, 0))
layout(matrix(c(1, 2, 1, 3), nrow = 2, ncol = 2), heights = c(0.5, 2, 2, 2))
#layout.show(3)
plot.new()
text(0.5,0.5,"DOX no BG - 17-3 24hr",cex = 2,font = 2)

boxplot(dox24hr17$Ind3_17_In_noBG ~ dox24hr17$Conc, 
        ylim = c(0, 80000), 
        ylab = "Cell Viability (RFLU)", 
        xlab = "Concentration (uM)", 
        main = "DOXORUBICIN 0hr 17-3 no BG"
)

boxplot(dox24hr17$Ind3_17_Fin_noBG ~ dox24hr17$Conc, 
        ylim = c(0,80000), 
        ylab = "Cell Viability (RFLU)", 
        xlab = "Concentration (uM)", 
        main = "DOXORUBICIN 24hr 17-3 no BG"
)

#####DMSO samples#####
#DMSO 78-1 24HR
par(mar = c(3.0, 3.0, 1.2, 1), mgp = c(2, .7, 0))
layout(matrix(c(1, 2, 1, 3), nrow = 2, ncol = 2), heights = c(0.5, 2, 2, 2))
#layout.show(3)
plot.new()
text(0.5,0.5,"DMSO no BG - 78-1 24hr",cex = 2,font = 2)

boxplot(dmso24hr78$Ind2_78_In_noBG ~ dmso24hr78$Conc, 
        ylim = c(0, 80000), 
        ylab = "Cell Viability (RFLU)", 
        xlab = "Concentration (uM)", 
        main = "DMSO VEHICLE 0hr 78-1 no BG"
)

boxplot(dmso24hr78$Ind2_78_Fin_noBG ~ dmso24hr78$Conc, 
        ylim = c(0,80000), 
        ylab = "Cell Viability (RFLU)", 
        xlab = "Concentration (uM)", 
        main = "DMSO VEHICLE 24hr 78-1 no BG"
)

#DMSO 75-1 no BG 24HR
par(mar = c(3.0, 3.0, 1.2, 1), mgp = c(2, .7, 0))
layout(matrix(c(1, 2, 1, 3), nrow = 2, ncol = 2), heights = c(0.5, 2, 2, 2))
#layout.show(3)
plot.new()
text(0.5,0.5,"DMSO no BG - 75-1 24hr",cex = 2,font = 2)

boxplot(dmso24hr75$Ind1_75_In_noBG ~ dmso24hr75$Conc, 
        ylim = c(0, 80000), 
        ylab = "Cell Viability (RFLU)", 
        xlab = "Concentration (uM)", 
        main = "DMSO VEHICLE 0hr 75-1 no BG"
)

boxplot(dmso24hr75$Ind1_75_Fin_noBG ~ dmso24hr75$Conc, 
        ylim = c(0,80000), 
        ylab = "Cell Viability (RFLU)", 
        xlab = "Concentration (uM)", 
        main = "DMSO VEHICLE 24hr 75-1 no BG"
)

#DMSO 17-3 no BG 24HR
par(mar = c(3.0, 3.0, 1.2, 1), mgp = c(2, .7, 0))
layout(matrix(c(1, 2, 1, 3), nrow = 2, ncol = 2), heights = c(0.5, 2, 2, 2))
#layout.show(3)
plot.new()
text(0.5,0.5,"DMSO no BG - 17-3 24hr",cex = 2,font = 2)

boxplot(dmso24hr17$Ind3_17_In_noBG ~ dmso24hr17$Conc, 
        ylim = c(0, 80000), 
        ylab = "Cell Viability (RFLU)", 
        xlab = "Concentration (uM)", 
        main = "DMSO VEHICLE 0hr 17-3 no BG"
)

boxplot(dmso24hr17$Ind3_17_Fin_noBG ~ dmso24hr17$Conc, 
        ylim = c(0,80000), 
        ylab = "Cell Viability (RFLU)", 
        xlab = "Concentration (uM)", 
        main = "DMSO VEHICLE 24hr 17-3 no BG"
)

```


```{r 5FU Samples BG removed 24hr, include=FALSE}
# #####FLUO samples#####
# #FLUO 78-1 no BG 24HR
# par(mar = c(3.0, 3.0, 1.2, 1), mgp = c(2, .7, 0))
# layout(matrix(c(1, 2, 1, 3), nrow = 2, ncol = 2), heights = c(0.5, 2, 2, 2))
# #layout.show(3)
# plot.new()
# text(0.5,0.5,"FLUO no BG - 78-1 24hr",cex = 2,font = 2)
# 
# boxplot(fluo24hr78$Ind2_78_In_noBG ~ fluo24hr78$Conc, 
#         ylim = c(0, 80000), 
#         ylab = "Cell Viability (RFLU)", 
#         xlab = "Concentration (uM)", 
#         main = "5-FLUOROURACIL 0hr 78-1 no BG"
# )
# 
# boxplot(fluo24hr78$Ind2_78_Fin_noBG ~ fluo24hr78$Conc, 
#         ylim = c(0,80000), 
#         ylab = "Cell Viability (RFLU)", 
#         xlab = "Concentration (uM)", 
#         main = "5-FLUOROURACIL 24hr 78-1 no BG"
# )
# 
# #FLUO 75-1 no BG 24HR
# par(mar = c(3.0, 3.0, 1.2, 1), mgp = c(2, .7, 0))
# layout(matrix(c(1, 2, 1, 3), nrow = 2, ncol = 2), heights = c(0.5, 2, 2, 2))
# #layout.show(3)
# plot.new()
# text(0.5,0.5,"FLUO no BG - 75-1 24hr",cex = 2,font = 2)
# 
# boxplot(fluo24hr75$Ind1_75_In_noBG ~ fluo24hr75$Conc, 
#         ylim = c(0, 80000), 
#         ylab = "Cell Viability (RFLU)", 
#         xlab = "Concentration (uM)", 
#         main = "5-FLUOROURACIL 0hr 75-1 no BG"
# )
# 
# boxplot(fluo24hr75$Ind1_75_Fin_noBG ~ fluo24hr75$Conc, 
#         ylim = c(0,80000), 
#         ylab = "Cell Viability (RFLU)", 
#         xlab = "Concentration (uM)", 
#         main = "5-FLUOROURACIL 24hr 75-1 no BG"
# )
# 
# #FLUO 17-3 no BG 24HR
# par(mar = c(3.0, 3.0, 1.2, 1), mgp = c(2, .7, 0))
# layout(matrix(c(1, 2, 1, 3), nrow = 2, ncol = 2), heights = c(0.5, 2, 2, 2))
# #layout.show(3)
# plot.new()
# text(0.5,0.5,"FLUO no BG - 17-3 24hr",cex = 2,font = 2)
# 
# boxplot(fluo24hr17$Ind3_17_In_noBG ~ fluo24hr17$Conc, 
#         ylim = c(0, 80000), 
#         ylab = "Cell Viability (RFLU)", 
#         xlab = "Concentration (uM)", 
#         main = "5-FLUOROURACIL 0hr 17-3 no BG"
# )
# 
# boxplot(fluo24hr17$Ind3_17_Fin_noBG ~ fluo24hr17$Conc, 
#         ylim = c(0, 80000), 
#         ylab = "Cell Viability (RFLU)", 
#         xlab = "Concentration (uM)", 
#         main = "5-FLUOROURACIL 24hr 17-3 no BG"
# )
```


```{r Boxplots BG Removed 48hr}
#####DOX Samples#####
#dox 78-1 no BG 48HR
par(mar = c(3.0, 3.0, 1.2, 1), mgp = c(2, .7, 0))
layout(matrix(c(1, 2, 1, 3), nrow = 2, ncol = 2), heights = c(0.5, 2, 2, 2))
#layout.show(3)
plot.new()
text(0.5,0.5,"DOX no BG - 78-1 48hr",cex = 2,font = 2)

boxplot(dox48hr78$Ind2_78_In_noBG ~ dox48hr78$Conc, 
        ylim = c(0, 80000), 
        ylab = "Cell Viability (RFLU)", 
        xlab = "Concentration (uM)", 
        main = "DOXORUBICIN 0hr 78-1 no BG"
)

boxplot(dox48hr78$Ind2_78_Fin_noBG ~ dox48hr78$Conc, 
        ylim = c(0,80000), 
        ylab = "Cell Viability (RFLU)", 
        xlab = "Concentration (uM)", 
        main = "DOXORUBICIN 48hr 78-1 no BG"
)

#dox 75-1 48HR
par(mar = c(3.0, 3.0, 1.2, 1), mgp = c(2, .7, 0))
layout(matrix(c(1, 2, 1, 3), nrow = 2, ncol = 2), heights = c(0.5, 2, 2, 2))
#layout.show(3)
plot.new()
text(0.5,0.5,"DOX no BG - 75-1 48hr",cex = 2,font = 2)

boxplot(dox48hr75$Ind1_75_In_noBG ~ dox48hr75$Conc, 
        ylim = c(0, 80000), 
        ylab = "Cell Viability (RFLU)", 
        xlab = "Concentration (uM)", 
        main = "DOXORUBICIN 0hr 75-1 no BG"
)

boxplot(dox48hr75$Ind1_75_Fin_noBG ~ dox48hr75$Conc, 
        ylim = c(0,80000), 
        ylab = "Cell Viability (RFLU)", 
        xlab = "Concentration (uM)", 
        main = "DOXORUBICIN 48hr 75-1 no BG"
)

#dox 17-3 48HR
par(mar = c(3.0, 3.0, 1.2, 1), mgp = c(2, .7, 0))
layout(matrix(c(1, 2, 1, 3), nrow = 2, ncol = 2), heights = c(0.5, 2, 2, 2))
#layout.show(3)
plot.new()
text(0.5,0.5,"DOX no BG - 17-3 48hr",cex = 2,font = 2)

boxplot(dox48hr17$Ind3_17_In_noBG ~ dox48hr17$Conc, 
        ylim = c(0, 80000), 
        ylab = "Cell Viability (RFLU)", 
        xlab = "Concentration (uM)", 
        main = "DOXORUBICIN 0hr 17-3 no BG"
)

boxplot(dox48hr17$Ind3_17_Fin_noBG ~ dox48hr17$Conc, 
        ylim = c(0,80000), 
        ylab = "Cell Viability (RFLU)", 
        xlab = "Concentration (uM)", 
        main = "DOXORUBICIN 48hr 17-3 no BG"
)

#####DMSO samples#####
#DMSO 78-1 48HR
par(mar = c(3.0, 3.0, 1.2, 1), mgp = c(2, .7, 0))
layout(matrix(c(1, 2, 1, 3), nrow = 2, ncol = 2), heights = c(0.5, 2, 2, 2))
#layout.show(3)
plot.new()
text(0.5,0.5,"DMSO no BG - 78-1 48hr",cex = 2,font = 2)

boxplot(dmso48hr78$Ind2_78_In_noBG ~ dmso48hr78$Conc, 
        ylim = c(0, 80000), 
        ylab = "Cell Viability (RFLU)", 
        xlab = "Concentration (uM)", 
        main = "DMSO VEHICLE 0hr 78-1 no BG"
)

boxplot(dmso48hr78$Ind2_78_Fin_noBG ~ dmso48hr78$Conc, 
        ylim = c(0,80000), 
        ylab = "Cell Viability (RFLU)", 
        xlab = "Concentration (uM)", 
        main = "DMSO VEHICLE 48hr 78-1"
)

#DMSO 75-1 no BG 48HR
par(mar = c(3.0, 3.0, 1.2, 1), mgp = c(2, .7, 0))
layout(matrix(c(1, 2, 1, 3), nrow = 2, ncol = 2), heights = c(0.5, 2, 2, 2))
#layout.show(3)
plot.new()
text(0.5,0.5,"DMSO no BG - 75-1 48hr",cex = 2,font = 2)

boxplot(dmso48hr75$Ind1_75_In_noBG ~ dmso48hr75$Conc, 
        ylim = c(0, 80000), 
        ylab = "Cell Viability (RFLU)", 
        xlab = "Concentration (uM)", 
        main = "DMSO VEHICLE 0hr 75-1 no BG"
)

boxplot(dmso48hr75$Ind1_75_Fin_noBG ~ dmso48hr75$Conc, 
        ylim = c(0,80000), 
        ylab = "Cell Viability (RFLU)", 
        xlab = "Concentration (uM)", 
        main = "DMSO VEHICLE 48hr 75-1 no BG"
)

#DMSO 17-3 no BG 48HR
par(mar = c(3.0, 3.0, 1.2, 1), mgp = c(2, .7, 0))
layout(matrix(c(1, 2, 1, 3), nrow = 2, ncol = 2), heights = c(0.5, 2, 2, 2))
#layout.show(3)
plot.new()
text(0.5,0.5,"DMSO no BG - 17-3 48hr",cex = 2,font = 2)

boxplot(dmso48hr17$Ind3_17_In_noBG ~ dmso48hr17$Conc, 
        ylim = c(0, 80000), 
        ylab = "Cell Viability (RFLU)", 
        xlab = "Concentration (uM)", 
        main = "DMSO VEHICLE 0hr 17-3 no BG"
)

boxplot(dmso48hr17$Ind3_17_Fin_noBG ~ dmso48hr17$Conc, 
        ylim = c(0,80000), 
        ylab = "Cell Viability (RFLU)", 
        xlab = "Concentration (uM)", 
        main = "DMSO VEHICLE 48hr 17-3 no BG"
)

```


```{r 5FU Samples BG Removed 48hr, include=FALSE}
# #####FLUO samples#####
# #FLUO 78-1 no BG 48HR
# par(mar = c(3.0, 3.0, 1.2, 1), mgp = c(2, .7, 0))
# layout(matrix(c(1, 2, 1, 3), nrow = 2, ncol = 2), heights = c(0.5, 2, 2, 2))
# #layout.show(3)
# plot.new()
# text(0.5,0.5,"FLUO no BG - 78-1 48hr",cex = 2,font = 2)
# 
# boxplot(fluo48hr78$Ind2_78_In_noBG ~ fluo48hr78$Conc, 
#         ylim = c(0, 80000), 
#         ylab = "Cell Viability (RFLU)", 
#         xlab = "Concentration (uM)", 
#         main = "5-FLUOROURACIL 0hr 78-1 no BG"
# )
# 
# boxplot(fluo48hr78$Ind2_78_Fin_noBG ~ fluo48hr78$Conc, 
#         ylim = c(0,80000), 
#         ylab = "Cell Viability (RFLU)", 
#         xlab = "Concentration (uM)", 
#         main = "5-FLUOROURACIL 48hr 78-1 no BG"
# )
# 
# #FLUO 75-1 no BG 48HR
# par(mar = c(3.0, 3.0, 1.2, 1), mgp = c(2, .7, 0))
# layout(matrix(c(1, 2, 1, 3), nrow = 2, ncol = 2), heights = c(0.5, 2, 2, 2))
# #layout.show(3)
# plot.new()
# text(0.5,0.5,"FLUO no BG - 75-1 48hr",cex = 2,font = 2)
# 
# boxplot(fluo48hr75$Ind1_75_In_noBG ~ fluo48hr75$Conc, 
#         ylim = c(0, 80000), 
#         ylab = "Cell Viability (RFLU)", 
#         xlab = "Concentration (uM)", 
#         main = "5-FLUOROURACIL 0hr 75-1 no BG"
# )
# 
# boxplot(fluo48hr75$Ind1_75_Fin_noBG ~ fluo48hr75$Conc, 
#         ylim = c(0,80000), 
#         ylab = "Cell Viability (RFLU)", 
#         xlab = "Concentration (uM)", 
#         main = "5-FLUOROURACIL 48hr 75-1 no BG"
# )
# 
# #FLUO 17-3 no BG 48HR
# par(mar = c(3.0, 3.0, 1.2, 1), mgp = c(2, .7, 0))
# layout(matrix(c(1, 2, 1, 3), nrow = 2, ncol = 2), heights = c(0.5, 2, 2, 2))
# #layout.show(3)
# plot.new()
# text(0.5,0.5,"FLUO no BG - 17-3 48hr",cex = 2,font = 2)
# 
# boxplot(fluo48hr17$Ind3_17_In_noBG ~ fluo48hr17$Conc, 
#         ylim = c(0, 80000), 
#         ylab = "Cell Viability (RFLU)", 
#         xlab = "Concentration (uM)", 
#         main = "5-FLUOROURACIL 0hr 17-3 no BG"
# )
# 
# boxplot(fluo48hr17$Ind3_17_Fin_noBG ~ fluo48hr17$Conc, 
#         ylim = c(0, 80000), 
#         ylab = "Cell Viability (RFLU)", 
#         xlab = "Concentration (uM)", 
#         main = "5-FLUOROURACIL 48hr 17-3 no BG"
# )

```


```{r Boxplots BG Removed 72hr}

#####DOX Samples#####
#dox 78-1 no BG 72HR
par(mar = c(3.0, 3.0, 1.2, 1), mgp = c(2, .7, 0))
layout(matrix(c(1, 2, 1, 3), nrow = 2, ncol = 2), heights = c(0.5, 2, 2, 2))
#layout.show(3)
plot.new()
text(0.5,0.5,"DOX no BG - 78-1 72hr",cex = 2,font = 2)

boxplot(dox72hr78$Ind2_78_In_noBG ~ dox72hr78$Conc, 
        ylim = c(0, 80000), 
        ylab = "Cell Viability (RFLU)", 
        xlab = "Concentration (uM)", 
        main = "DOXORUBICIN 0hr 78-1 no BG"
)

boxplot(dox72hr78$Ind2_78_Fin_noBG ~ dox72hr78$Conc, 
        ylim = c(0,80000), 
        ylab = "Cell Viability (RFLU)", 
        xlab = "Concentration (uM)", 
        main = "DOXORUBICIN 72hr 78-1 no BG"
)

#dox 75-1 72HR
par(mar = c(3.0, 3.0, 1.2, 1), mgp = c(2, .7, 0))
layout(matrix(c(1, 2, 1, 3), nrow = 2, ncol = 2), heights = c(0.5, 2, 2, 2))
#layout.show(3)
plot.new()
text(0.5,0.5,"DOX no BG - 75-1 72hr",cex = 2,font = 2)

boxplot(dox72hr75$Ind1_75_In_noBG ~ dox72hr75$Conc, 
        ylim = c(0, 80000), 
        ylab = "Cell Viability (RFLU)", 
        xlab = "Concentration (uM)", 
        main = "DOXORUBICIN 0hr 75-1 no BG"
)

boxplot(dox72hr75$Ind1_75_Fin_noBG ~ dox72hr75$Conc, 
        ylim = c(0,80000), 
        ylab = "Cell Viability (RFLU)", 
        xlab = "Concentration (uM)", 
        main = "DOXORUBICIN 72hr 75-1 no BG"
)

#dox 17-3 72HR
par(mar = c(3.0, 3.0, 1.2, 1), mgp = c(2, .7, 0))
layout(matrix(c(1, 2, 1, 3), nrow = 2, ncol = 2), heights = c(0.5, 2, 2, 2))
#layout.show(3)
plot.new()
text(0.5,0.5,"DOX no BG - 17-3 72hr",cex = 2,font = 2)

boxplot(dox72hr17$Ind3_17_In_noBG ~ dox72hr17$Conc, 
        ylim = c(0, 80000), 
        ylab = "Cell Viability (RFLU)", 
        xlab = "Concentration (uM)", 
        main = "DOXORUBICIN 0hr 17-3 no BG"
)

boxplot(dox72hr17$Ind3_17_Fin_noBG ~ dox72hr17$Conc, 
        ylim = c(0,80000), 
        ylab = "Cell Viability (RFLU)", 
        xlab = "Concentration (uM)", 
        main = "DOXORUBICIN 72hr 17-3 no BG"
)

#####DMSO samples#####
#DMSO 78-1 72HR
par(mar = c(3.0, 3.0, 1.2, 1), mgp = c(2, .7, 0))
layout(matrix(c(1, 2, 1, 3), nrow = 2, ncol = 2), heights = c(0.5, 2, 2, 2))
#layout.show(3)
plot.new()
text(0.5,0.5,"DMSO no BG - 78-1 72hr",cex = 2,font = 2)

boxplot(dmso72hr78$Ind2_78_In_noBG ~ dmso72hr78$Conc, 
        ylim = c(0, 80000), 
        ylab = "Cell Viability (RFLU)", 
        xlab = "Concentration (uM)", 
        main = "DMSO VEHICLE 0hr 78-1 no BG"
)

boxplot(dmso72hr78$Ind2_78_Fin_noBG ~ dmso72hr78$Conc, 
        ylim = c(0,80000), 
        ylab = "Cell Viability (RFLU)", 
        xlab = "Concentration (uM)", 
        main = "DMSO VEHICLE 72hr 78-1"
)

#DMSO 75-1 no BG 72HR
par(mar = c(3.0, 3.0, 1.2, 1), mgp = c(2, .7, 0))
layout(matrix(c(1, 2, 1, 3), nrow = 2, ncol = 2), heights = c(0.5, 2, 2, 2))
#layout.show(3)
plot.new()
text(0.5,0.5,"DMSO no BG - 75-1 72hr",cex = 2,font = 2)

boxplot(dmso72hr75$Ind1_75_In_noBG ~ dmso72hr75$Conc, 
        ylim = c(0, 80000), 
        ylab = "Cell Viability (RFLU)", 
        xlab = "Concentration (uM)", 
        main = "DMSO VEHICLE 0hr 75-1 no BG"
)

boxplot(dmso72hr75$Ind1_75_Fin_noBG ~ dmso72hr75$Conc, 
        ylim = c(0,80000), 
        ylab = "Cell Viability (RFLU)", 
        xlab = "Concentration (uM)", 
        main = "DMSO VEHICLE 72hr 75-1 no BG"
)

#DMSO 17-3 no BG 72HR
par(mar = c(3.0, 3.0, 1.2, 1), mgp = c(2, .7, 0))
layout(matrix(c(1, 2, 1, 3), nrow = 2, ncol = 2), heights = c(0.5, 2, 2, 2))
#layout.show(3)
plot.new()
text(0.5,0.5,"DMSO no BG - 17-3 72hr",cex = 2,font = 2)

boxplot(dmso72hr17$Ind3_17_In_noBG ~ dmso72hr17$Conc, 
        ylim = c(0, 80000), 
        ylab = "Cell Viability (RFLU)", 
        xlab = "Concentration (uM)", 
        main = "DMSO VEHICLE 0hr 17-3 no BG"
)

boxplot(dmso72hr17$Ind3_17_Fin_noBG ~ dmso72hr17$Conc, 
        ylim = c(0,80000), 
        ylab = "Cell Viability (RFLU)", 
        xlab = "Concentration (uM)", 
        main = "DMSO VEHICLE 72hr 17-3 no BG"
)
```

```{r 5FU Samples BG Removed 72hr, include=FALSE}
# #####FLUO samples#####
# #FLUO 78-1 no BG 72HR
# par(mar = c(3.0, 3.0, 1.2, 1), mgp = c(2, .7, 0))
# layout(matrix(c(1, 2, 1, 3), nrow = 2, ncol = 2), heights = c(0.5, 2, 2, 2))
# #layout.show(3)
# plot.new()
# text(0.5,0.5,"FLUO no BG - 78-1 72hr",cex = 2,font = 2)
# 
# boxplot(fluo72hr78$Ind2_78_In_noBG ~ fluo72hr78$Conc, 
#         ylim = c(0, 80000), 
#         ylab = "Cell Viability (RFLU)", 
#         xlab = "Concentration (uM)", 
#         main = "5-FLUOROURACIL 0hr 78-1 no BG"
# )
# 
# boxplot(fluo72hr78$Ind2_78_Fin_noBG ~ fluo72hr78$Conc, 
#         ylim = c(0,80000), 
#         ylab = "Cell Viability (RFLU)", 
#         xlab = "Concentration (uM)", 
#         main = "5-FLUOROURACIL 72hr 78-1 no BG"
# )
# 
# #FLUO 75-1 no BG 72HR
# par(mar = c(3.0, 3.0, 1.2, 1), mgp = c(2, .7, 0))
# layout(matrix(c(1, 2, 1, 3), nrow = 2, ncol = 2), heights = c(0.5, 2, 2, 2))
# #layout.show(3)
# plot.new()
# text(0.5,0.5,"FLUO no BG - 75-1 72hr",cex = 2,font = 2)
# 
# boxplot(fluo72hr75$Ind1_75_In_noBG ~ fluo72hr75$Conc, 
#         ylim = c(0, 80000), 
#         ylab = "Cell Viability (RFLU)", 
#         xlab = "Concentration (uM)", 
#         main = "5-FLUOROURACIL 0hr 75-1 no BG"
# )
# 
# boxplot(fluo72hr75$Ind1_75_Fin_noBG ~ fluo72hr75$Conc, 
#         ylim = c(0,80000), 
#         ylab = "Cell Viability (RFLU)", 
#         xlab = "Concentration (uM)", 
#         main = "5-FLUOROURACIL 72hr 75-1 no BG"
# )
# 
# #FLUO 17-3 no BG 72HR
# par(mar = c(3.0, 3.0, 1.2, 1), mgp = c(2, .7, 0))
# layout(matrix(c(1, 2, 1, 3), nrow = 2, ncol = 2), heights = c(0.5, 2, 2, 2))
# #layout.show(3)
# plot.new()
# text(0.5,0.5,"FLUO no BG - 17-3 72hr",cex = 2,font = 2)
# 
# boxplot(fluo72hr17$Ind3_17_In_noBG ~ fluo72hr17$Conc, 
#         ylim = c(0, 80000), 
#         ylab = "Cell Viability (RFLU)", 
#         xlab = "Concentration (uM)", 
#         main = "5-FLUOROURACIL 0hr 17-3 no BG"
# )
# 
# boxplot(fluo72hr17$Ind3_17_Fin_noBG ~ fluo72hr17$Conc, 
#         ylim = c(0, 80000), 
#         ylab = "Cell Viability (RFLU)", 
#         xlab = "Concentration (uM)", 
#         main = "5-FLUOROURACIL 72hr 17-3 no BG"
# )

```


Now let's plot the next step: subtracting the empty wells
```{r Boxplots Empty Wells Removed 24hr}
#####DOX Samples#####
#dox 78-1 Empty Wells 24HR
par(mar = c(3.0, 3.0, 1.2, 1), mgp = c(2, .7, 0))
layout(matrix(c(1, 2, 1, 3), nrow = 2, ncol = 2), heights = c(0.5, 2, 2, 2))
#layout.show(3)
plot.new()
text(0.5,0.5,"DOX no BG Empty - 78-1 24hr",cex = 2,font = 2)

boxplot(dox24hr78$Ind2_78_In_noBG_Low ~ dox24hr78$Conc, 
        ylim = c(0, 1.5), 
        ylab = "Cell Viability (%)", 
        xlab = "Concentration (uM)", 
        main = "DOXORUBICIN 0hr 78-1 no BG Empty"
)

boxplot(dox24hr78$Ind2_78_Fin_noBG_Low ~ dox24hr78$Conc, 
        ylim = c(0, 1.5), 
        ylab = "Cell Viability (%)", 
        xlab = "Concentration (uM)", 
        main = "DOXORUBICIN 24hr 78-1 no BG"
)

#dox 75-1 24HR
par(mar = c(3.0, 3.0, 1.2, 1), mgp = c(2, .7, 0))
layout(matrix(c(1, 2, 1, 3), nrow = 2, ncol = 2), heights = c(0.5, 2, 2, 2))
#layout.show(3)
plot.new()
text(0.5,0.5,"DOX no BG Empty - 75-1 24hr",cex = 2,font = 2)

boxplot(dox24hr75$Ind1_75_In_noBG_Low ~ dox24hr75$Conc, 
        ylim = c(0, 1.5), 
        ylab = "Cell Viability (%)", 
        xlab = "Concentration (uM)", 
        main = "DOXORUBICIN 0hr 75-1 no BG Empty"
)

boxplot(dox24hr75$Ind1_75_Fin_noBG_Low ~ dox24hr75$Conc, 
        ylim = c(0, 1.5), 
        ylab = "Cell Viability (%)", 
        xlab = "Concentration (uM)", 
        main = "DOXORUBICIN 24hr 75-1 no BG Empty"
)

#dox 17-3 24HR
par(mar = c(3.0, 3.0, 1.2, 1), mgp = c(2, .7, 0))
layout(matrix(c(1, 2, 1, 3), nrow = 2, ncol = 2), heights = c(0.5, 2, 2, 2))
#layout.show(3)
plot.new()
text(0.5,0.5,"DOX no BG Empty - 17-3 24hr",cex = 2,font = 2)

boxplot(dox24hr17$Ind3_17_In_noBG_Low ~ dox24hr17$Conc, 
        ylim = c(0, 1.5), 
        ylab = "Cell Viability (%)", 
        xlab = "Concentration (uM)", 
        main = "DOXORUBICIN 0hr 17-3 no BG Empty"
)

boxplot(dox24hr17$Ind3_17_Fin_noBG_Low ~ dox24hr17$Conc, 
        ylim = c(0, 1.5), 
        ylab = "Cell Viability (%)", 
        xlab = "Concentration (uM)", 
        main = "DOXORUBICIN 24hr 17-3 no BG Empty"
)

#####DMSO samples#####
#DMSO 78-1 24HR
par(mar = c(3.0, 3.0, 1.2, 1), mgp = c(2, .7, 0))
layout(matrix(c(1, 2, 1, 3), nrow = 2, ncol = 2), heights = c(0.5, 2, 2, 2))
#layout.show(3)
plot.new()
text(0.5,0.5,"DMSO no BG Empty - 78-1 24hr",cex = 2,font = 2)

boxplot(dmso24hr78$Ind2_78_In_noBG_Low ~ dmso24hr78$Conc, 
        ylim = c(0, 1.5), 
        ylab = "Cell Viability (%)", 
        xlab = "Concentration (uM)", 
        main = "DMSO VEHICLE 0hr 78-1 no BG Empty"
)

boxplot(dmso24hr78$Ind2_78_Fin_noBG_Low ~ dmso24hr78$Conc, 
        ylim = c(0, 1.5), 
        ylab = "Cell Viability (%)", 
        xlab = "Concentration (uM)", 
        main = "DMSO VEHICLE 24hr 78-1 no BG Empty"
)

#DMSO 75-1 no BG Empty 24HR
par(mar = c(3.0, 3.0, 1.2, 1), mgp = c(2, .7, 0))
layout(matrix(c(1, 2, 1, 3), nrow = 2, ncol = 2), heights = c(0.5, 2, 2, 2))
#layout.show(3)
plot.new()
text(0.5,0.5,"DMSO no BG Empty - 75-1 24hr",cex = 2,font = 2)

boxplot(dmso24hr75$Ind1_75_In_noBG_Low ~ dmso24hr75$Conc, 
        ylim = c(0, 1.5), 
        ylab = "Cell Viability (%)", 
        xlab = "Concentration (uM)", 
        main = "DMSO VEHICLE 0hr 75-1 no BG Empty"
)

boxplot(dmso24hr75$Ind1_75_Fin_noBG_Low ~ dmso24hr75$Conc, 
        ylim = c(0, 1.5), 
        ylab = "Cell Viability (%)", 
        xlab = "Concentration (uM)", 
        main = "DMSO VEHICLE 24hr 75-1 no BG Empty"
)

#DMSO 17-3 no BG Empty 24HR
par(mar = c(3.0, 3.0, 1.2, 1), mgp = c(2, .7, 0))
layout(matrix(c(1, 2, 1, 3), nrow = 2, ncol = 2), heights = c(0.5, 2, 2, 2))
#layout.show(3)
plot.new()
text(0.5,0.5,"DMSO no BG Empty - 17-3 24hr",cex = 2,font = 2)

boxplot(dmso24hr17$Ind3_17_In_noBG_Low ~ dmso24hr17$Conc, 
        ylim = c(0, 1.5), 
        ylab = "Cell Viability (%)", 
        xlab = "Concentration (uM)", 
        main = "DMSO VEHICLE 0hr 17-3 no BG Empty"
)

boxplot(dmso24hr17$Ind3_17_Fin_noBG_Low ~ dmso24hr17$Conc, 
        ylim = c(0, 1.5), 
        ylab = "Cell Viability (%)", 
        xlab = "Concentration (uM)", 
        main = "DMSO VEHICLE 24hr 17-3 no BG Empty"
)

```

```{r 5FU Samples Empty Well Removed 24hr, include=FALSE}
# #####FLUO samples#####
# #FLUO 78-1 no BG 24HR
# par(mar = c(3.0, 3.0, 1.2, 1), mgp = c(2, .7, 0))
# layout(matrix(c(1, 2, 1, 3), nrow = 2, ncol = 2), heights = c(0.5, 2, 2, 2))
# #layout.show(3)
# plot.new()
# text(0.5,0.5,"FLUO no BG Empty - 78-1 24hr",cex = 2,font = 2)
# 
# boxplot(fluo24hr78$Ind2_78_In_noBG_Low ~ fluo24hr78$Conc, 
#         ylim = c(0, 1.5), 
#         ylab = "Cell Viability (%)", 
#         xlab = "Concentration (uM)", 
#         main = "5-FLUOROURACIL 0hr 78-1 no BG Empty"
# )
# 
# boxplot(fluo24hr78$Ind2_78_Fin_noBG_Low ~ fluo24hr78$Conc, 
#         ylim = c(0, 1.5), 
#         ylab = "Cell Viability (%)", 
#         xlab = "Concentration (uM)", 
#         main = "5-FLUOROURACIL 24hr 78-1 no BG Empty"
# )
# 
# #FLUO 75-1 no BG Empty 24HR
# par(mar = c(3.0, 3.0, 1.2, 1), mgp = c(2, .7, 0))
# layout(matrix(c(1, 2, 1, 3), nrow = 2, ncol = 2), heights = c(0.5, 2, 2, 2))
# #layout.show(3)
# plot.new()
# text(0.5,0.5,"FLUO no BG Empty - 75-1 24hr",cex = 2,font = 2)
# 
# boxplot(fluo24hr75$Ind1_75_In_noBG_Low ~ fluo24hr75$Conc, 
#         ylim = c(0, 1.5), 
#         ylab = "Cell Viability (%)", 
#         xlab = "Concentration (uM)", 
#         main = "5-FLUOROURACIL 0hr 75-1 no BG Empty"
# )
# 
# boxplot(fluo24hr75$Ind1_75_Fin_noBG_Low ~ fluo24hr75$Conc, 
#         ylim = c(0, 1.5), 
#         ylab = "Cell Viability (%)", 
#         xlab = "Concentration (uM)", 
#         main = "5-FLUOROURACIL 24hr 75-1 no BG Empty"
# )
# 
# #FLUO 17-3 no BG Empty 24HR
# par(mar = c(3.0, 3.0, 1.2, 1), mgp = c(2, .7, 0))
# layout(matrix(c(1, 2, 1, 3), nrow = 2, ncol = 2), heights = c(0.5, 2, 2, 2))
# #layout.show(3)
# plot.new()
# text(0.5,0.5,"FLUO no BG Empty - 17-3 24hr",cex = 2,font = 2)
# 
# boxplot(fluo24hr17$Ind3_17_In_noBG_Low ~ fluo24hr17$Conc, 
#         ylim = c(0, 1.5), 
#         ylab = "Cell Viability (%)", 
#         xlab = "Concentration (uM)", 
#         main = "5-FLUOROURACIL 0hr 17-3 no BG Empty"
# )
# 
# boxplot(fluo24hr17$Ind3_17_Fin_noBG_Low ~ fluo24hr17$Conc, 
#         ylim = c(0, 1.5), 
#         ylab = "Cell Viability (%)", 
#         xlab = "Concentration (uM)", 
#         main = "5-FLUOROURACIL 24hr 17-3 no BG Empty"
# )

```



```{r Boxplots Empty Wells Removed 48hr}
#####DOX Samples#####
#dox 78-1 Empty Wells 48HR
par(mar = c(3.0, 3.0, 1.2, 1), mgp = c(2, .7, 0))
layout(matrix(c(1, 2, 1, 3), nrow = 2, ncol = 2), heights = c(0.5, 2, 2, 2))
#layout.show(3)
plot.new()
text(0.5,0.5,"DOX no BG Empty - 78-1 48hr",cex = 2,font = 2)

boxplot(dox48hr78$Ind2_78_In_noBG_Low ~ dox48hr78$Conc, 
        ylim = c(0, 1.5), 
        ylab = "Cell Viability (%)", 
        xlab = "Concentration (uM)", 
        main = "DOXORUBICIN 0hr 78-1 no BG Empty"
)

boxplot(dox48hr78$Ind2_78_Fin_noBG_Low ~ dox48hr78$Conc, 
        ylim = c(0, 1.5), 
        ylab = "Cell Viability (%)", 
        xlab = "Concentration (uM)", 
        main = "DOXORUBICIN 48hr 78-1 no BG"
)

#dox 75-1 48HR
par(mar = c(3.0, 3.0, 1.2, 1), mgp = c(2, .7, 0))
layout(matrix(c(1, 2, 1, 3), nrow = 2, ncol = 2), heights = c(0.5, 2, 2, 2))
#layout.show(3)
plot.new()
text(0.5,0.5,"DOX no BG Empty - 75-1 48hr",cex = 2,font = 2)

boxplot(dox48hr75$Ind1_75_In_noBG_Low ~ dox48hr75$Conc, 
        ylim = c(0, 1.5), 
        ylab = "Cell Viability (%)", 
        xlab = "Concentration (uM)", 
        main = "DOXORUBICIN 0hr 75-1 no BG Empty"
)

boxplot(dox48hr75$Ind1_75_Fin_noBG_Low ~ dox48hr75$Conc, 
        ylim = c(0, 1.5), 
        ylab = "Cell Viability (%)", 
        xlab = "Concentration (uM)", 
        main = "DOXORUBICIN 48hr 75-1 no BG Empty"
)

#dox 17-3 48HR
par(mar = c(3.0, 3.0, 1.2, 1), mgp = c(2, .7, 0))
layout(matrix(c(1, 2, 1, 3), nrow = 2, ncol = 2), heights = c(0.5, 2, 2, 2))
#layout.show(3)
plot.new()
text(0.5,0.5,"DOX no BG Empty - 17-3 48hr",cex = 2,font = 2)

boxplot(dox48hr17$Ind3_17_In_noBG_Low ~ dox48hr17$Conc, 
        ylim = c(0, 1.5), 
        ylab = "Cell Viability (%)", 
        xlab = "Concentration (uM)", 
        main = "DOXORUBICIN 0hr 17-3 no BG Empty"
)

boxplot(dox48hr17$Ind3_17_Fin_noBG_Low ~ dox48hr17$Conc, 
        ylim = c(0, 1.5), 
        ylab = "Cell Viability (%)", 
        xlab = "Concentration (uM)", 
        main = "DOXORUBICIN 48hr 17-3 no BG Empty"
)

#####DMSO samples#####
#DMSO 78-1 48HR
par(mar = c(3.0, 3.0, 1.2, 1), mgp = c(2, .7, 0))
layout(matrix(c(1, 2, 1, 3), nrow = 2, ncol = 2), heights = c(0.5, 2, 2, 2))
#layout.show(3)
plot.new()
text(0.5,0.5,"DMSO no BG Empty - 78-1 48hr",cex = 2,font = 2)

boxplot(dmso48hr78$Ind2_78_In_noBG_Low ~ dmso48hr78$Conc, 
        ylim = c(0, 1.5), 
        ylab = "Cell Viability (%)", 
        xlab = "Concentration (uM)", 
        main = "DMSO VEHICLE 0hr 78-1 no BG Empty"
)

boxplot(dmso48hr78$Ind2_78_Fin_noBG_Low ~ dmso48hr78$Conc, 
        ylim = c(0, 1.5), 
        ylab = "Cell Viability (%)", 
        xlab = "Concentration (uM)", 
        main = "DMSO VEHICLE 48hr 78-1 no BG Empty"
)

#DMSO 75-1 no BG Empty 48HR
par(mar = c(3.0, 3.0, 1.2, 1), mgp = c(2, .7, 0))
layout(matrix(c(1, 2, 1, 3), nrow = 2, ncol = 2), heights = c(0.5, 2, 2, 2))
#layout.show(3)
plot.new()
text(0.5,0.5,"DMSO no BG Empty - 75-1 48hr",cex = 2,font = 2)

boxplot(dmso48hr75$Ind1_75_In_noBG_Low ~ dmso48hr75$Conc, 
        ylim = c(0, 1.5), 
        ylab = "Cell Viability (%)", 
        xlab = "Concentration (uM)", 
        main = "DMSO VEHICLE 0hr 75-1 no BG Empty"
)

boxplot(dmso48hr75$Ind1_75_Fin_noBG_Low ~ dmso48hr75$Conc, 
        ylim = c(0, 1.5), 
        ylab = "Cell Viability (%)", 
        xlab = "Concentration (uM)", 
        main = "DMSO VEHICLE 48hr 75-1 no BG Empty"
)

#DMSO 17-3 no BG Empty 48HR
par(mar = c(3.0, 3.0, 1.2, 1), mgp = c(2, .7, 0))
layout(matrix(c(1, 2, 1, 3), nrow = 2, ncol = 2), heights = c(0.5, 2, 2, 2))
#layout.show(3)
plot.new()
text(0.5,0.5,"DMSO no BG Empty - 17-3 48hr",cex = 2,font = 2)

boxplot(dmso48hr17$Ind3_17_In_noBG_Low ~ dmso48hr17$Conc, 
        ylim = c(0, 1.5), 
        ylab = "Cell Viability (%)", 
        xlab = "Concentration (uM)", 
        main = "DMSO VEHICLE 0hr 17-3 no BG Empty"
)

boxplot(dmso48hr17$Ind3_17_Fin_noBG_Low ~ dmso48hr17$Conc, 
        ylim = c(0, 1.5), 
        ylab = "Cell Viability (%)", 
        xlab = "Concentration (uM)", 
        main = "DMSO VEHICLE 48hr 17-3 no BG Empty"
)
```

```{r 5FU Samples Empty Wells Removed 48hr}
# #####FLUO samples#####
# #FLUO 78-1 no BG 48HR
# par(mar = c(3.0, 3.0, 1.2, 1), mgp = c(2, .7, 0))
# layout(matrix(c(1, 2, 1, 3), nrow = 2, ncol = 2), heights = c(0.5, 2, 2, 2))
# #layout.show(3)
# plot.new()
# text(0.5,0.5,"FLUO no BG Empty - 78-1 48hr",cex = 2,font = 2)
# 
# boxplot(fluo48hr78$Ind2_78_In_noBG_Low ~ fluo48hr78$Conc, 
#         ylim = c(0, 1.5), 
#         ylab = "Cell Viability (%)", 
#         xlab = "Concentration (uM)", 
#         main = "5-FLUOROURACIL 0hr 78-1 no BG Empty"
# )
# 
# boxplot(fluo48hr78$Ind2_78_Fin_noBG_Low ~ fluo48hr78$Conc, 
#         ylim = c(0, 1.5), 
#         ylab = "Cell Viability (%)", 
#         xlab = "Concentration (uM)", 
#         main = "5-FLUOROURACIL 48hr 78-1 no BG Empty"
# )
# 
# #FLUO 75-1 no BG Empty 48HR
# par(mar = c(3.0, 3.0, 1.2, 1), mgp = c(2, .7, 0))
# layout(matrix(c(1, 2, 1, 3), nrow = 2, ncol = 2), heights = c(0.5, 2, 2, 2))
# #layout.show(3)
# plot.new()
# text(0.5,0.5,"FLUO no BG Empty - 75-1 48hr",cex = 2,font = 2)
# 
# boxplot(fluo48hr75$Ind1_75_In_noBG_Low ~ fluo48hr75$Conc, 
#         ylim = c(0, 1.5), 
#         ylab = "Cell Viability (%)", 
#         xlab = "Concentration (uM)", 
#         main = "5-FLUOROURACIL 0hr 75-1 no BG Empty"
# )
# 
# boxplot(fluo48hr75$Ind1_75_Fin_noBG_Low ~ fluo48hr75$Conc, 
#         ylim = c(0, 1.5), 
#         ylab = "Cell Viability (%)", 
#         xlab = "Concentration (uM)", 
#         main = "5-FLUOROURACIL 48hr 75-1 no BG Empty"
# )
# 
# #FLUO 17-3 no BG Empty 48HR
# par(mar = c(3.0, 3.0, 1.2, 1), mgp = c(2, .7, 0))
# layout(matrix(c(1, 2, 1, 3), nrow = 2, ncol = 2), heights = c(0.5, 2, 2, 2))
# #layout.show(3)
# plot.new()
# text(0.5,0.5,"FLUO no BG Empty - 17-3 48hr",cex = 2,font = 2)
# 
# boxplot(fluo48hr17$Ind3_17_In_noBG_Low ~ fluo48hr17$Conc, 
#         ylim = c(0, 1.5), 
#         ylab = "Cell Viability (%)", 
#         xlab = "Concentration (uM)", 
#         main = "5-FLUOROURACIL 0hr 17-3 no BG Empty"
# )
# 
# boxplot(fluo48hr17$Ind3_17_Fin_noBG_Low ~ fluo48hr17$Conc, 
#         ylim = c(0, 1.5), 
#         ylab = "Cell Viability (%)", 
#         xlab = "Concentration (uM)", 
#         main = "5-FLUOROURACIL 48hr 17-3 no BG Empty"
# )

```


```{r Boxplots Empty Wells Removed 72hr}
#####DOX Samples#####
#dox 78-1 Empty Wells 72HR
par(mar = c(3.0, 3.0, 1.2, 1), mgp = c(2, .7, 0))
layout(matrix(c(1, 2, 1, 3), nrow = 2, ncol = 2), heights = c(0.5, 2, 2, 2))
#layout.show(3)
plot.new()
text(0.5,0.5,"DOX no BG Empty - 78-1 72hr",cex = 2,font = 2)

boxplot(dox72hr78$Ind2_78_In_noBG_Low ~ dox72hr78$Conc, 
        ylim = c(0, 1.5), 
        ylab = "Cell Viability (%)", 
        xlab = "Concentration (uM)", 
        main = "DOXORUBICIN 0hr 78-1 no BG Empty"
)

boxplot(dox72hr78$Ind2_78_Fin_noBG_Low ~ dox72hr78$Conc, 
        ylim = c(0, 1.5), 
        ylab = "Cell Viability (%)", 
        xlab = "Concentration (uM)", 
        main = "DOXORUBICIN 72hr 78-1 no BG"
)

#dox 75-1 72HR
par(mar = c(3.0, 3.0, 1.2, 1), mgp = c(2, .7, 0))
layout(matrix(c(1, 2, 1, 3), nrow = 2, ncol = 2), heights = c(0.5, 2, 2, 2))
#layout.show(3)
plot.new()
text(0.5,0.5,"DOX no BG Empty - 75-1 72hr",cex = 2,font = 2)

boxplot(dox72hr75$Ind1_75_In_noBG_Low ~ dox72hr75$Conc, 
        ylim = c(0, 1.5), 
        ylab = "Cell Viability (%)", 
        xlab = "Concentration (uM)", 
        main = "DOXORUBICIN 0hr 75-1 no BG Empty"
)

boxplot(dox72hr75$Ind1_75_Fin_noBG_Low ~ dox72hr75$Conc, 
        ylim = c(0, 1.5), 
        ylab = "Cell Viability (%)", 
        xlab = "Concentration (uM)", 
        main = "DOXORUBICIN 72hr 75-1 no BG Empty"
)

#dox 17-3 72HR
par(mar = c(3.0, 3.0, 1.2, 1), mgp = c(2, .7, 0))
layout(matrix(c(1, 2, 1, 3), nrow = 2, ncol = 2), heights = c(0.5, 2, 2, 2))
#layout.show(3)
plot.new()
text(0.5,0.5,"DOX no BG Empty - 17-3 72hr",cex = 2,font = 2)

boxplot(dox72hr17$Ind3_17_In_noBG_Low ~ dox72hr17$Conc, 
        ylim = c(0, 1.5), 
        ylab = "Cell Viability (%)", 
        xlab = "Concentration (uM)", 
        main = "DOXORUBICIN 0hr 17-3 no BG Empty"
)

boxplot(dox72hr17$Ind3_17_Fin_noBG_Low ~ dox72hr17$Conc, 
        ylim = c(0, 1.5), 
        ylab = "Cell Viability (%)", 
        xlab = "Concentration (uM)", 
        main = "DOXORUBICIN 72hr 17-3 no BG Empty"
)

#####DMSO samples#####
#DMSO 78-1 72HR
par(mar = c(3.0, 3.0, 1.2, 1), mgp = c(2, .7, 0))
layout(matrix(c(1, 2, 1, 3), nrow = 2, ncol = 2), heights = c(0.5, 2, 2, 2))
#layout.show(3)
plot.new()
text(0.5,0.5,"DMSO no BG Empty - 78-1 72hr",cex = 2,font = 2)

boxplot(dmso72hr78$Ind2_78_In_noBG_Low ~ dmso72hr78$Conc, 
        ylim = c(0, 1.5), 
        ylab = "Cell Viability (%)", 
        xlab = "Concentration (uM)", 
        main = "DMSO VEHICLE 0hr 78-1 no BG Empty"
)

boxplot(dmso72hr78$Ind2_78_Fin_noBG_Low ~ dmso72hr78$Conc, 
        ylim = c(0, 1.5), 
        ylab = "Cell Viability (%)", 
        xlab = "Concentration (uM)", 
        main = "DMSO VEHICLE 72hr 78-1 no BG Empty"
)

#DMSO 75-1 no BG Empty 72HR
par(mar = c(3.0, 3.0, 1.2, 1), mgp = c(2, .7, 0))
layout(matrix(c(1, 2, 1, 3), nrow = 2, ncol = 2), heights = c(0.5, 2, 2, 2))
#layout.show(3)
plot.new()
text(0.5,0.5,"DMSO no BG Empty - 75-1 72hr",cex = 2,font = 2)

boxplot(dmso72hr75$Ind1_75_In_noBG_Low ~ dmso72hr75$Conc, 
        ylim = c(0, 1.5), 
        ylab = "Cell Viability (%)", 
        xlab = "Concentration (uM)", 
        main = "DMSO VEHICLE 0hr 75-1 no BG Empty"
)

boxplot(dmso72hr75$Ind1_75_Fin_noBG_Low ~ dmso72hr75$Conc, 
        ylim = c(0, 1.5), 
        ylab = "Cell Viability (%)", 
        xlab = "Concentration (uM)", 
        main = "DMSO VEHICLE 72hr 75-1 no BG Empty"
)

#DMSO 17-3 no BG Empty 72HR
par(mar = c(3.0, 3.0, 1.2, 1), mgp = c(2, .7, 0))
layout(matrix(c(1, 2, 1, 3), nrow = 2, ncol = 2), heights = c(0.5, 2, 2, 2))
#layout.show(3)
plot.new()
text(0.5,0.5,"DMSO no BG Empty - 17-3 72hr",cex = 2,font = 2)

boxplot(dmso72hr17$Ind3_17_In_noBG_Low ~ dmso72hr17$Conc, 
        ylim = c(0, 1.5), 
        ylab = "Cell Viability (%)", 
        xlab = "Concentration (uM)", 
        main = "DMSO VEHICLE 0hr 17-3 no BG Empty"
)

boxplot(dmso72hr17$Ind3_17_Fin_noBG_Low ~ dmso72hr17$Conc, 
        ylim = c(0, 1.5), 
        ylab = "Cell Viability (%)", 
        xlab = "Concentration (uM)", 
        main = "DMSO VEHICLE 72hr 17-3 no BG Empty"
)
```


```{r 5FU Samples no bg empty 72hr, include=FALSE}
# #####FLUO samples#####
# #FLUO 78-1 no BG 72HR
# par(mar = c(3.0, 3.0, 1.2, 1), mgp = c(2, .7, 0))
# layout(matrix(c(1, 2, 1, 3), nrow = 2, ncol = 2), heights = c(0.5, 2, 2, 2))
# #layout.show(3)
# plot.new()
# text(0.5,0.5,"FLUO no BG Empty - 78-1 72hr",cex = 2,font = 2)
# 
# boxplot(fluo72hr78$Ind2_78_In_noBG_Low ~ fluo72hr78$Conc, 
#         ylim = c(0, 1.5), 
#         ylab = "Cell Viability (%)", 
#         xlab = "Concentration (uM)", 
#         main = "5-FLUOROURACIL 0hr 78-1 no BG Empty"
# )
# 
# boxplot(fluo72hr78$Ind2_78_Fin_noBG_Low ~ fluo72hr78$Conc, 
#         ylim = c(0, 1.5), 
#         ylab = "Cell Viability (%)", 
#         xlab = "Concentration (uM)", 
#         main = "5-FLUOROURACIL 72hr 78-1 no BG Empty"
# )
# 
# #FLUO 75-1 no BG Empty 72HR
# par(mar = c(3.0, 3.0, 1.2, 1), mgp = c(2, .7, 0))
# layout(matrix(c(1, 2, 1, 3), nrow = 2, ncol = 2), heights = c(0.5, 2, 2, 2))
# #layout.show(3)
# plot.new()
# text(0.5,0.5,"FLUO no BG Empty - 75-1 72hr",cex = 2,font = 2)
# 
# boxplot(fluo72hr75$Ind1_75_In_noBG_Low ~ fluo72hr75$Conc, 
#         ylim = c(0, 1.5), 
#         ylab = "Cell Viability (%)", 
#         xlab = "Concentration (uM)", 
#         main = "5-FLUOROURACIL 0hr 75-1 no BG Empty"
# )
# 
# boxplot(fluo72hr75$Ind1_75_Fin_noBG_Low ~ fluo72hr75$Conc, 
#         ylim = c(0, 1.5), 
#         ylab = "Cell Viability (%)", 
#         xlab = "Concentration (uM)", 
#         main = "5-FLUOROURACIL 72hr 75-1 no BG Empty"
# )
# 
# #FLUO 17-3 no BG Empty 72HR
# par(mar = c(3.0, 3.0, 1.2, 1), mgp = c(2, .7, 0))
# layout(matrix(c(1, 2, 1, 3), nrow = 2, ncol = 2), heights = c(0.5, 2, 2, 2))
# #layout.show(3)
# plot.new()
# text(0.5,0.5,"FLUO no BG Empty - 17-3 72hr",cex = 2,font = 2)
# 
# boxplot(fluo72hr17$Ind3_17_In_noBG_Low ~ fluo72hr17$Conc, 
#         ylim = c(0, 1.5), 
#         ylab = "Cell Viability (%)", 
#         xlab = "Concentration (uM)", 
#         main = "5-FLUOROURACIL 0hr 17-3 no BG Empty"
# )
# 
# boxplot(fluo72hr17$Ind3_17_Fin_noBG_Low ~ fluo72hr17$Conc, 
#         ylim = c(0, 1.5), 
#         ylab = "Cell Viability (%)", 
#         xlab = "Concentration (uM)", 
#         main = "5-FLUOROURACIL 72hr 17-3 no BG Empty"
# )

```


Now let's plot the third step: dividing the matched vehicle values
```{r Boxplots Matched Vehicle Divided 24hr}
#####DOX Samples#####
#dox 78-1 Veh 24HR
par(mar = c(3.0, 3.0, 1.2, 1), mgp = c(2, .7, 0))
layout(matrix(c(1, 2, 1, 3), nrow = 2, ncol = 2), heights = c(0.5, 2, 2, 2))
#layout.show(3)
plot.new()
text(0.5,0.5,"DOX no BG Empty Veh - 78-1 24hr",cex = 2,font = 2)

boxplot(dox24hr78$Ind2_78_In_noBG_Low_Veh ~ dox24hr78$Conc, 
        ylim = c(0, 1.5), 
        ylab = "Cell Viability (%)", 
        xlab = "Concentration (uM)", 
        main = "DOXORUBICIN 0hr 78-1 no BG Empty Veh"
)

boxplot(dox24hr78$Ind2_78_Fin_noBG_Low_Veh ~ dox24hr78$Conc, 
        ylim = c(0, 1.5), 
        ylab = "Cell Viability (%)", 
        xlab = "Concentration (uM)", 
        main = "DOXORUBICIN 24hr 78-1 no BG Veh"
)

#dox 75-1 24HR
par(mar = c(3.0, 3.0, 1.2, 1), mgp = c(2, .7, 0))
layout(matrix(c(1, 2, 1, 3), nrow = 2, ncol = 2), heights = c(0.5, 2, 2, 2))
#layout.show(3)
plot.new()
text(0.5,0.5,"DOX no BG Empty Veh - 75-1 24hr",cex = 2,font = 2)

boxplot(dox24hr75$Ind1_75_In_noBG_Low_Veh ~ dox24hr75$Conc, 
        ylim = c(0, 1.5), 
        ylab = "Cell Viability (%)", 
        xlab = "Concentration (uM)", 
        main = "DOXORUBICIN 0hr 75-1 no BG Empty Veh"
)

boxplot(dox24hr75$Ind1_75_Fin_noBG_Low_Veh ~ dox24hr75$Conc, 
        ylim = c(0, 1.5), 
        ylab = "Cell Viability (%)", 
        xlab = "Concentration (uM)", 
        main = "DOXORUBICIN 24hr 75-1 no BG Empty Veh"
)

#dox 17-3 24HR
par(mar = c(3.0, 3.0, 1.2, 1), mgp = c(2, .7, 0))
layout(matrix(c(1, 2, 1, 3), nrow = 2, ncol = 2), heights = c(0.5, 2, 2, 2))
#layout.show(3)
plot.new()
text(0.5,0.5,"DOX no BG Empty Veh - 17-3 24hr",cex = 2,font = 2)

boxplot(dox24hr17$Ind3_17_In_noBG_Low_Veh ~ dox24hr17$Conc, 
        ylim = c(0, 1.5), 
        ylab = "Cell Viability (%)", 
        xlab = "Concentration (uM)", 
        main = "DOXORUBICIN 0hr 17-3 no BG Empty Veh"
)

boxplot(dox24hr17$Ind3_17_Fin_noBG_Low_Veh ~ dox24hr17$Conc, 
        ylim = c(0, 1.5), 
        ylab = "Cell Viability (%)", 
        xlab = "Concentration (uM)", 
        main = "DOXORUBICIN 24hr 17-3 no BG Empty Veh"
)

#####DMSO samples#####
#DMSO 78-1 24HR
par(mar = c(3.0, 3.0, 1.2, 1), mgp = c(2, .7, 0))
layout(matrix(c(1, 2, 1, 3), nrow = 2, ncol = 2), heights = c(0.5, 2, 2, 2))
#layout.show(3)
plot.new()
text(0.5,0.5,"DMSO no BG Empty Veh - 78-1 24hr",cex = 2,font = 2)

boxplot(dmso24hr78$Ind2_78_In_noBG_Low_Veh ~ dmso24hr78$Conc, 
        ylim = c(0, 1.5), 
        ylab = "Cell Viability (%)", 
        xlab = "Concentration (uM)", 
        main = "DMSO VEHICLE 0hr 78-1 no BG Empty Veh"
)

boxplot(dmso24hr78$Ind2_78_Fin_noBG_Low_Veh ~ dmso24hr78$Conc, 
        ylim = c(0, 1.5), 
        ylab = "Cell Viability (%)", 
        xlab = "Concentration (uM)", 
        main = "DMSO VEHICLE 24hr 78-1 no BG Empty Veh"
)

#DMSO 75-1 no BG Empty 24HR
par(mar = c(3.0, 3.0, 1.2, 1), mgp = c(2, .7, 0))
layout(matrix(c(1, 2, 1, 3), nrow = 2, ncol = 2), heights = c(0.5, 2, 2, 2))
#layout.show(3)
plot.new()
text(0.5,0.5,"DMSO no BG Empty Veh - 75-1 24hr",cex = 2,font = 2)

boxplot(dmso24hr75$Ind1_75_In_noBG_Low_Veh ~ dmso24hr75$Conc, 
        ylim = c(0, 1.5), 
        ylab = "Cell Viability (%)", 
        xlab = "Concentration (uM)", 
        main = "DMSO VEHICLE 0hr 75-1 no BG Empty Veh"
)

boxplot(dmso24hr75$Ind1_75_Fin_noBG_Low_Veh ~ dmso24hr75$Conc, 
        ylim = c(0, 1.5), 
        ylab = "Cell Viability (%)", 
        xlab = "Concentration (uM)", 
        main = "DMSO VEHICLE 24hr 75-1 no BG Empty Veh"
)

#DMSO 17-3 no BG Empty 24HR
par(mar = c(3.0, 3.0, 1.2, 1), mgp = c(2, .7, 0))
layout(matrix(c(1, 2, 1, 3), nrow = 2, ncol = 2), heights = c(0.5, 2, 2, 2))
#layout.show(3)
plot.new()
text(0.5,0.5,"DMSO no BG Empty Veh - 17-3 24hr",cex = 2,font = 2)

boxplot(dmso24hr17$Ind3_17_In_noBG_Low_Veh ~ dmso24hr17$Conc, 
        ylim = c(0, 1.5), 
        ylab = "Cell Viability (%)", 
        xlab = "Concentration (uM)", 
        main = "DMSO VEHICLE 0hr 17-3 no BG Empty Veh"
)

boxplot(dmso24hr17$Ind3_17_Fin_noBG_Low_Veh ~ dmso24hr17$Conc, 
        ylim = c(0, 1.5), 
        ylab = "Cell Viability (%)", 
        xlab = "Concentration (uM)", 
        main = "DMSO VEHICLE 24hr 17-3 no BG Empty Veh"
)

```

```{r 5FU Samples Matched Vehicle noBG 24hr, include=FALSE}
# #####FLUO samples#####
# #FLUO 78-1 no BG 24HR
# par(mar = c(3.0, 3.0, 1.2, 1), mgp = c(2, .7, 0))
# layout(matrix(c(1, 2, 1, 3), nrow = 2, ncol = 2), heights = c(0.5, 2, 2, 2))
# #layout.show(3)
# plot.new()
# text(0.5,0.5,"FLUO no BG Empty Veh - 78-1 24hr",cex = 2,font = 2)
# 
# boxplot(fluo24hr78$Ind2_78_In_noBG_Low_Veh ~ fluo24hr78$Conc, 
#         ylim = c(0, 1.5), 
#         ylab = "Cell Viability (%)", 
#         xlab = "Concentration (uM)", 
#         main = "5-FLUOROURACIL 0hr 78-1 no BG Empty Veh"
# )
# 
# boxplot(fluo24hr78$Ind2_78_Fin_noBG_Low_Veh ~ fluo24hr78$Conc, 
#         ylim = c(0, 1.5), 
#         ylab = "Cell Viability (%)", 
#         xlab = "Concentration (uM)", 
#         main = "5-FLUOROURACIL 24hr 78-1 no BG Empty Veh"
# )
# 
# #FLUO 75-1 no BG Empty 24HR
# par(mar = c(3.0, 3.0, 1.2, 1), mgp = c(2, .7, 0))
# layout(matrix(c(1, 2, 1, 3), nrow = 2, ncol = 2), heights = c(0.5, 2, 2, 2))
# #layout.show(3)
# plot.new()
# text(0.5,0.5,"FLUO no BG Empty Veh - 75-1 24hr",cex = 2,font = 2)
# 
# boxplot(fluo24hr75$Ind1_75_In_noBG_Low_Veh ~ fluo24hr75$Conc, 
#         ylim = c(0, 1.5), 
#         ylab = "Cell Viability (%)", 
#         xlab = "Concentration (uM)", 
#         main = "5-FLUOROURACIL 0hr 75-1 no BG Empty Veh"
# )
# 
# boxplot(fluo24hr75$Ind1_75_Fin_noBG_Low_Veh ~ fluo24hr75$Conc, 
#         ylim = c(0, 1.5), 
#         ylab = "Cell Viability (%)", 
#         xlab = "Concentration (uM)", 
#         main = "5-FLUOROURACIL 24hr 75-1 no BG Empty Veh"
# )
# 
# #FLUO 17-3 no BG Empty 24HR
# par(mar = c(3.0, 3.0, 1.2, 1), mgp = c(2, .7, 0))
# layout(matrix(c(1, 2, 1, 3), nrow = 2, ncol = 2), heights = c(0.5, 2, 2, 2))
# #layout.show(3)
# plot.new()
# text(0.5,0.5,"FLUO no BG Empty Veh - 17-3 24hr",cex = 2,font = 2)
# 
# boxplot(fluo24hr17$Ind3_17_In_noBG_Low_Veh ~ fluo24hr17$Conc, 
#         ylim = c(0, 1.5), 
#         ylab = "Cell Viability (%)", 
#         xlab = "Concentration (uM)", 
#         main = "5-FLUOROURACIL 0hr 17-3 no BG Empty Veh"
# )
# 
# boxplot(fluo24hr17$Ind3_17_Fin_noBG_Low_Veh ~ fluo24hr17$Conc, 
#         ylim = c(0, 1.5), 
#         ylab = "Cell Viability (%)", 
#         xlab = "Concentration (uM)", 
#         main = "5-FLUOROURACIL 24hr 17-3 no BG Empty Veh"
# )
```


```{r Boxplots Matched Vehicle Divided 48hr}
#####DOX Samples#####
#dox 78-1 Veh 48HR
par(mar = c(3.0, 3.0, 1.2, 1), mgp = c(2, .7, 0))
layout(matrix(c(1, 2, 1, 3), nrow = 2, ncol = 2), heights = c(0.5, 2, 2, 2))
#layout.show(3)
plot.new()
text(0.5,0.5,"DOX no BG Empty Veh - 78-1 48hr",cex = 2,font = 2)

boxplot(dox48hr78$Ind2_78_In_noBG_Low_Veh ~ dox48hr78$Conc, 
        ylim = c(0, 1.5), 
        ylab = "Cell Viability (%)", 
        xlab = "Concentration (uM)", 
        main = "DOXORUBICIN 0hr 78-1 no BG Empty Veh"
)

boxplot(dox48hr78$Ind2_78_Fin_noBG_Low_Veh ~ dox48hr78$Conc, 
        ylim = c(0, 1.5), 
        ylab = "Cell Viability (%)", 
        xlab = "Concentration (uM)", 
        main = "DOXORUBICIN 48hr 78-1 no BG Veh"
)

#dox 75-1 48HR
par(mar = c(3.0, 3.0, 1.2, 1), mgp = c(2, .7, 0))
layout(matrix(c(1, 2, 1, 3), nrow = 2, ncol = 2), heights = c(0.5, 2, 2, 2))
#layout.show(3)
plot.new()
text(0.5,0.5,"DOX no BG Empty Veh - 75-1 48hr",cex = 2,font = 2)

boxplot(dox48hr75$Ind1_75_In_noBG_Low_Veh ~ dox48hr75$Conc, 
        ylim = c(0, 1.5), 
        ylab = "Cell Viability (%)", 
        xlab = "Concentration (uM)", 
        main = "DOXORUBICIN 0hr 75-1 no BG Empty Veh"
)

boxplot(dox48hr75$Ind1_75_Fin_noBG_Low_Veh ~ dox48hr75$Conc, 
        ylim = c(0, 1.5), 
        ylab = "Cell Viability (%)", 
        xlab = "Concentration (uM)", 
        main = "DOXORUBICIN 48hr 75-1 no BG Empty Veh"
)

#dox 17-3 48HR
par(mar = c(3.0, 3.0, 1.2, 1), mgp = c(2, .7, 0))
layout(matrix(c(1, 2, 1, 3), nrow = 2, ncol = 2), heights = c(0.5, 2, 2, 2))
#layout.show(3)
plot.new()
text(0.5,0.5,"DOX no BG Empty Veh - 17-3 48hr",cex = 2,font = 2)

boxplot(dox48hr17$Ind3_17_In_noBG_Low_Veh ~ dox48hr17$Conc, 
        ylim = c(0, 1.5), 
        ylab = "Cell Viability (%)", 
        xlab = "Concentration (uM)", 
        main = "DOXORUBICIN 0hr 17-3 no BG Empty Veh"
)

boxplot(dox48hr17$Ind3_17_Fin_noBG_Low_Veh ~ dox48hr17$Conc, 
        ylim = c(0, 1.5), 
        ylab = "Cell Viability (%)", 
        xlab = "Concentration (uM)", 
        main = "DOXORUBICIN 48hr 17-3 no BG Empty Veh"
)

#####DMSO samples#####
#DMSO 78-1 48HR
par(mar = c(3.0, 3.0, 1.2, 1), mgp = c(2, .7, 0))
layout(matrix(c(1, 2, 1, 3), nrow = 2, ncol = 2), heights = c(0.5, 2, 2, 2))
#layout.show(3)
plot.new()
text(0.5,0.5,"DMSO no BG Empty Veh - 78-1 48hr",cex = 2,font = 2)

boxplot(dmso48hr78$Ind2_78_In_noBG_Low_Veh ~ dmso48hr78$Conc, 
        ylim = c(0, 1.5), 
        ylab = "Cell Viability (%)", 
        xlab = "Concentration (uM)", 
        main = "DMSO VEHICLE 0hr 78-1 no BG Empty Veh"
)

boxplot(dmso48hr78$Ind2_78_Fin_noBG_Low_Veh ~ dmso48hr78$Conc, 
        ylim = c(0, 1.5), 
        ylab = "Cell Viability (%)", 
        xlab = "Concentration (uM)", 
        main = "DMSO VEHICLE 48hr 78-1 no BG Empty Veh"
)

#DMSO 75-1 no BG Empty 48HR
par(mar = c(3.0, 3.0, 1.2, 1), mgp = c(2, .7, 0))
layout(matrix(c(1, 2, 1, 3), nrow = 2, ncol = 2), heights = c(0.5, 2, 2, 2))
#layout.show(3)
plot.new()
text(0.5,0.5,"DMSO no BG Empty Veh - 75-1 48hr",cex = 2,font = 2)

boxplot(dmso48hr75$Ind1_75_In_noBG_Low_Veh ~ dmso48hr75$Conc, 
        ylim = c(0, 1.5), 
        ylab = "Cell Viability (%)", 
        xlab = "Concentration (uM)", 
        main = "DMSO VEHICLE 0hr 75-1 no BG Empty Veh"
)

boxplot(dmso48hr75$Ind1_75_Fin_noBG_Low_Veh ~ dmso48hr75$Conc, 
        ylim = c(0, 1.5), 
        ylab = "Cell Viability (%)", 
        xlab = "Concentration (uM)", 
        main = "DMSO VEHICLE 48hr 75-1 no BG Empty Veh"
)

#DMSO 17-3 no BG Empty 48HR
par(mar = c(3.0, 3.0, 1.2, 1), mgp = c(2, .7, 0))
layout(matrix(c(1, 2, 1, 3), nrow = 2, ncol = 2), heights = c(0.5, 2, 2, 2))
#layout.show(3)
plot.new()
text(0.5,0.5,"DMSO no BG Empty Veh - 17-3 48hr",cex = 2,font = 2)

boxplot(dmso48hr17$Ind3_17_In_noBG_Low_Veh ~ dmso48hr17$Conc, 
        ylim = c(0, 1.5), 
        ylab = "Cell Viability (%)", 
        xlab = "Concentration (uM)", 
        main = "DMSO VEHICLE 0hr 17-3 no BG Empty Veh"
)

boxplot(dmso48hr17$Ind3_17_Fin_noBG_Low_Veh ~ dmso48hr17$Conc, 
        ylim = c(0, 1.5), 
        ylab = "Cell Viability (%)", 
        xlab = "Concentration (uM)", 
        main = "DMSO VEHICLE 48hr 17-3 no BG Empty Veh"
)
```

```{r 5FU Samples Boxplots 48hr Matched Veh Div, include=FALSE}
#####FLUO samples#####
#FLUO 78-1 no BG 48HR
par(mar = c(3.0, 3.0, 1.2, 1), mgp = c(2, .7, 0))
layout(matrix(c(1, 2, 1, 3), nrow = 2, ncol = 2), heights = c(0.5, 2, 2, 2))
#layout.show(3)
plot.new()
text(0.5,0.5,"FLUO no BG Empty Veh - 78-1 48hr",cex = 2,font = 2)

boxplot(fluo48hr78$Ind2_78_In_noBG_Low_Veh ~ fluo48hr78$Conc, 
        ylim = c(0, 1.5), 
        ylab = "Cell Viability (%)", 
        xlab = "Concentration (uM)", 
        main = "5-FLUOROURACIL 0hr 78-1 no BG Empty Veh"
)

boxplot(fluo48hr78$Ind2_78_Fin_noBG_Low_Veh ~ fluo48hr78$Conc, 
        ylim = c(0, 1.5), 
        ylab = "Cell Viability (%)", 
        xlab = "Concentration (uM)", 
        main = "5-FLUOROURACIL 48hr 78-1 no BG Empty Veh"
)

#FLUO 75-1 no BG Empty 48HR
par(mar = c(3.0, 3.0, 1.2, 1), mgp = c(2, .7, 0))
layout(matrix(c(1, 2, 1, 3), nrow = 2, ncol = 2), heights = c(0.5, 2, 2, 2))
#layout.show(3)
plot.new()
text(0.5,0.5,"FLUO no BG Empty Veh - 75-1 48hr",cex = 2,font = 2)

boxplot(fluo48hr75$Ind1_75_In_noBG_Low_Veh ~ fluo48hr75$Conc, 
        ylim = c(0, 1.5), 
        ylab = "Cell Viability (%)", 
        xlab = "Concentration (uM)", 
        main = "5-FLUOROURACIL 0hr 75-1 no BG Empty Veh"
)

boxplot(fluo48hr75$Ind1_75_Fin_noBG_Low_Veh ~ fluo48hr75$Conc, 
        ylim = c(0, 1.5), 
        ylab = "Cell Viability (%)", 
        xlab = "Concentration (uM)", 
        main = "5-FLUOROURACIL 48hr 75-1 no BG Empty Veh"
)

#FLUO 17-3 no BG Empty 48HR
par(mar = c(3.0, 3.0, 1.2, 1), mgp = c(2, .7, 0))
layout(matrix(c(1, 2, 1, 3), nrow = 2, ncol = 2), heights = c(0.5, 2, 2, 2))
#layout.show(3)
plot.new()
text(0.5,0.5,"FLUO no BG Empty Veh - 17-3 48hr",cex = 2,font = 2)

boxplot(fluo48hr17$Ind3_17_In_noBG_Low_Veh ~ fluo48hr17$Conc, 
        ylim = c(0, 1.5), 
        ylab = "Cell Viability (%)", 
        xlab = "Concentration (uM)", 
        main = "5-FLUOROURACIL 0hr 17-3 no BG Empty Veh"
)

boxplot(fluo48hr17$Ind3_17_Fin_noBG_Low_Veh ~ fluo48hr17$Conc, 
        ylim = c(0, 1.5), 
        ylab = "Cell Viability (%)", 
        xlab = "Concentration (uM)", 
        main = "5-FLUOROURACIL 48hr 17-3 no BG Empty Veh"
)
```


```{r Boxplots Matched Vehicle Divided 72hr}
#####DOX Samples#####
#dox 78-1 Veh 72HR
par(mar = c(3.0, 3.0, 1.2, 1), mgp = c(2, .7, 0))
layout(matrix(c(1, 2, 1, 3), nrow = 2, ncol = 2), heights = c(0.5, 2, 2, 2))
#layout.show(3)
plot.new()
text(0.5,0.5,"DOX no BG Empty Veh - 78-1 72hr",cex = 2,font = 2)

boxplot(dox72hr78$Ind2_78_In_noBG_Low_Veh ~ dox72hr78$Conc, 
        ylim = c(0, 1.5), 
        ylab = "Cell Viability (%)", 
        xlab = "Concentration (uM)", 
        main = "DOXORUBICIN 0hr 78-1 no BG Empty Veh"
)

boxplot(dox72hr78$Ind2_78_Fin_noBG_Low_Veh ~ dox72hr78$Conc, 
        ylim = c(0, 1.5), 
        ylab = "Cell Viability (%)", 
        xlab = "Concentration (uM)", 
        main = "DOXORUBICIN 72hr 78-1 no BG Veh"
)

#dox 75-1 72HR
par(mar = c(3.0, 3.0, 1.2, 1), mgp = c(2, .7, 0))
layout(matrix(c(1, 2, 1, 3), nrow = 2, ncol = 2), heights = c(0.5, 2, 2, 2))
#layout.show(3)
plot.new()
text(0.5,0.5,"DOX no BG Empty Veh - 75-1 72hr",cex = 2,font = 2)

boxplot(dox72hr75$Ind1_75_In_noBG_Low_Veh ~ dox72hr75$Conc, 
        ylim = c(0, 1.5), 
        ylab = "Cell Viability (%)", 
        xlab = "Concentration (uM)", 
        main = "DOXORUBICIN 0hr 75-1 no BG Empty Veh"
)

boxplot(dox72hr75$Ind1_75_Fin_noBG_Low_Veh ~ dox72hr75$Conc, 
        ylim = c(0, 1.5), 
        ylab = "Cell Viability (%)", 
        xlab = "Concentration (uM)", 
        main = "DOXORUBICIN 72hr 75-1 no BG Empty Veh"
)

#dox 17-3 72HR
par(mar = c(3.0, 3.0, 1.2, 1), mgp = c(2, .7, 0))
layout(matrix(c(1, 2, 1, 3), nrow = 2, ncol = 2), heights = c(0.5, 2, 2, 2))
#layout.show(3)
plot.new()
text(0.5,0.5,"DOX no BG Empty Veh - 17-3 72hr",cex = 2,font = 2)

boxplot(dox72hr17$Ind3_17_In_noBG_Low_Veh ~ dox72hr17$Conc, 
        ylim = c(0, 1.5), 
        ylab = "Cell Viability (%)", 
        xlab = "Concentration (uM)", 
        main = "DOXORUBICIN 0hr 17-3 no BG Empty Veh"
)

boxplot(dox72hr17$Ind3_17_Fin_noBG_Low_Veh ~ dox72hr17$Conc, 
        ylim = c(0, 1.5), 
        ylab = "Cell Viability (%)", 
        xlab = "Concentration (uM)", 
        main = "DOXORUBICIN 72hr 17-3 no BG Empty Veh"
)

#####DMSO samples#####
#DMSO 78-1 72HR
par(mar = c(3.0, 3.0, 1.2, 1), mgp = c(2, .7, 0))
layout(matrix(c(1, 2, 1, 3), nrow = 2, ncol = 2), heights = c(0.5, 2, 2, 2))
#layout.show(3)
plot.new()
text(0.5,0.5,"DMSO no BG Empty Veh - 78-1 72hr",cex = 2,font = 2)

boxplot(dmso72hr78$Ind2_78_In_noBG_Low_Veh ~ dmso72hr78$Conc, 
        ylim = c(0, 1.5), 
        ylab = "Cell Viability (%)", 
        xlab = "Concentration (uM)", 
        main = "DMSO VEHICLE 0hr 78-1 no BG Empty Veh"
)

boxplot(dmso72hr78$Ind2_78_Fin_noBG_Low_Veh ~ dmso72hr78$Conc, 
        ylim = c(0, 1.5), 
        ylab = "Cell Viability (%)", 
        xlab = "Concentration (uM)", 
        main = "DMSO VEHICLE 72hr 78-1 no BG Empty Veh"
)

#DMSO 75-1 no BG Empty 72HR
par(mar = c(3.0, 3.0, 1.2, 1), mgp = c(2, .7, 0))
layout(matrix(c(1, 2, 1, 3), nrow = 2, ncol = 2), heights = c(0.5, 2, 2, 2))
#layout.show(3)
plot.new()
text(0.5,0.5,"DMSO no BG Empty Veh - 75-1 72hr",cex = 2,font = 2)

boxplot(dmso72hr75$Ind1_75_In_noBG_Low_Veh ~ dmso72hr75$Conc, 
        ylim = c(0, 1.5), 
        ylab = "Cell Viability (%)", 
        xlab = "Concentration (uM)", 
        main = "DMSO VEHICLE 0hr 75-1 no BG Empty Veh"
)

boxplot(dmso72hr75$Ind1_75_Fin_noBG_Low_Veh ~ dmso72hr75$Conc, 
        ylim = c(0, 1.5), 
        ylab = "Cell Viability (%)", 
        xlab = "Concentration (uM)", 
        main = "DMSO VEHICLE 72hr 75-1 no BG Empty Veh"
)

#DMSO 17-3 no BG Empty 72HR
par(mar = c(3.0, 3.0, 1.2, 1), mgp = c(2, .7, 0))
layout(matrix(c(1, 2, 1, 3), nrow = 2, ncol = 2), heights = c(0.5, 2, 2, 2))
#layout.show(3)
plot.new()
text(0.5,0.5,"DMSO no BG Empty Veh - 17-3 72hr",cex = 2,font = 2)

boxplot(dmso72hr17$Ind3_17_In_noBG_Low_Veh ~ dmso72hr17$Conc, 
        ylim = c(0, 1.5), 
        ylab = "Cell Viability (%)", 
        xlab = "Concentration (uM)", 
        main = "DMSO VEHICLE 0hr 17-3 no BG Empty Veh"
)

boxplot(dmso72hr17$Ind3_17_Fin_noBG_Low_Veh ~ dmso72hr17$Conc, 
        ylim = c(0, 1.5), 
        ylab = "Cell Viability (%)", 
        xlab = "Concentration (uM)", 
        main = "DMSO VEHICLE 72hr 17-3 no BG Empty Veh"
)
```

```{r 5FU Samples Boxplots 72hr noBG, include=FALSE}
# #####FLUO samples#####
# #FLUO 78-1 no BG 72HR
# par(mar = c(3.0, 3.0, 1.2, 1), mgp = c(2, .7, 0))
# layout(matrix(c(1, 2, 1, 3), nrow = 2, ncol = 2), heights = c(0.5, 2, 2, 2))
# #layout.show(3)
# plot.new()
# text(0.5,0.5,"FLUO no BG Empty Veh - 78-1 72hr",cex = 2,font = 2)
# 
# boxplot(fluo72hr78$Ind2_78_In_noBG_Low_Veh ~ fluo72hr78$Conc, 
#         ylim = c(0, 1.5), 
#         ylab = "Cell Viability (%)", 
#         xlab = "Concentration (uM)", 
#         main = "5-FLUOROURACIL 0hr 78-1 no BG Empty Veh"
# )
# 
# boxplot(fluo72hr78$Ind2_78_Fin_noBG_Low_Veh ~ fluo72hr78$Conc, 
#         ylim = c(0, 1.5), 
#         ylab = "Cell Viability (%)", 
#         xlab = "Concentration (uM)", 
#         main = "5-FLUOROURACIL 72hr 78-1 no BG Empty Veh"
# )
# 
# #FLUO 75-1 no BG Empty 72HR
# par(mar = c(3.0, 3.0, 1.2, 1), mgp = c(2, .7, 0))
# layout(matrix(c(1, 2, 1, 3), nrow = 2, ncol = 2), heights = c(0.5, 2, 2, 2))
# #layout.show(3)
# plot.new()
# text(0.5,0.5,"FLUO no BG Empty Veh - 75-1 72hr",cex = 2,font = 2)
# 
# boxplot(fluo72hr75$Ind1_75_In_noBG_Low_Veh ~ fluo72hr75$Conc, 
#         ylim = c(0, 1.5), 
#         ylab = "Cell Viability (%)", 
#         xlab = "Concentration (uM)", 
#         main = "5-FLUOROURACIL 0hr 75-1 no BG Empty Veh"
# )
# 
# boxplot(fluo72hr75$Ind1_75_Fin_noBG_Low_Veh ~ fluo72hr75$Conc, 
#         ylim = c(0, 1.5), 
#         ylab = "Cell Viability (%)", 
#         xlab = "Concentration (uM)", 
#         main = "5-FLUOROURACIL 72hr 75-1 no BG Empty Veh"
# )
# 
# #FLUO 17-3 no BG Empty 72HR
# par(mar = c(3.0, 3.0, 1.2, 1), mgp = c(2, .7, 0))
# layout(matrix(c(1, 2, 1, 3), nrow = 2, ncol = 2), heights = c(0.5, 2, 2, 2))
# #layout.show(3)
# plot.new()
# text(0.5,0.5,"FLUO no BG Empty Veh - 17-3 72hr",cex = 2,font = 2)
# 
# boxplot(fluo72hr17$Ind3_17_In_noBG_Low_Veh ~ fluo72hr17$Conc, 
#         ylim = c(0, 1.5), 
#         ylab = "Cell Viability (%)", 
#         xlab = "Concentration (uM)", 
#         main = "5-FLUOROURACIL 0hr 17-3 no BG Empty Veh"
# )
# 
# boxplot(fluo72hr17$Ind3_17_Fin_noBG_Low_Veh ~ fluo72hr17$Conc, 
#         ylim = c(0, 1.5), 
#         ylab = "Cell Viability (%)", 
#         xlab = "Concentration (uM)", 
#         main = "5-FLUOROURACIL 72hr 17-3 no BG Empty Veh"
# )
```


Now for the final step, dividing the final timepoint by the initial baseline reading at 0hr
```{r Boxplots Final Data 24hr}
#####DOX Samples#####
#dox All 24HR
par(mar = c(3.0, 3.0, 1.2, 1), mgp = c(2, .7, 0))
layout(matrix(c(1, 2, 1, 3, 1, 4), nrow = 2, ncol = 3), heights = c(0.5, 2, 2, 2))
#layout.show(3)
plot.new()
text(0.5,0.5,"DOXORUBICIN - 24hr",cex = 2,font = 2)

boxplot(dox24hr78$Ind2_78_Div ~ dox24hr78$Conc, 
        ylim = c(0, 1.5), 
        ylab = "Cell Viability (%)", 
        xlab = "Concentration (uM)", 
        main = "78-1 Div"
)

boxplot(dox24hr75$Ind1_75_Div ~ dox24hr75$Conc, 
        ylim = c(0, 1.5), 
        ylab = "Cell Viability (%)", 
        xlab = "Concentration (uM)", 
        main = "75-1 Div"
)

boxplot(dox24hr17$Ind3_17_Div ~ dox24hr17$Conc, 
        ylim = c(0, 1.5), 
        ylab = "Cell Viability (%)", 
        xlab = "Concentration (uM)", 
        main = "17-3 Div"
)

#####DMSO samples#####
#DMSO All 24HR
par(mar = c(3.0, 3.0, 1.2, 1), mgp = c(2, .7, 0))
layout(matrix(c(1, 2, 1, 3, 1, 4), nrow = 2, ncol = 3), heights = c(0.5, 2, 2, 2))
#layout.show(3)
plot.new()
text(0.5,0.5,"DMSO VEHICLE - 24hr",cex = 2,font = 2)

boxplot(dmso24hr78$Ind2_78_Div ~ dmso24hr78$Conc, 
        ylim = c(0, 1.5), 
        ylab = "Cell Viability (%)", 
        xlab = "Concentration (uM)", 
        main = "78-1 Div"
)

boxplot(dmso24hr75$Ind1_75_Div ~ dmso24hr75$Conc, 
        ylim = c(0, 1.5), 
        ylab = "Cell Viability (%)", 
        xlab = "Concentration (uM)", 
        main = "75-1 Div"
)

boxplot(dmso24hr17$Ind3_17_Div ~ dmso24hr17$Conc, 
        ylim = c(0, 1.5), 
        ylab = "Cell Viability (%)", 
        xlab = "Concentration (uM)", 
        main = "17-3 Div"
)
```

```{r 5FU Boxplots 24hr, include=FALSE}

# #####FLUO samples#####
# par(mar = c(3.0, 3.0, 1.2, 1), mgp = c(2, .7, 0))
# layout(matrix(c(1, 2, 1, 3, 1, 4), nrow = 2, ncol = 3), heights = c(0.5, 2, 2, 2))
# #layout.show(3)
# plot.new()
# text(0.5,0.5,"5-FLUOROURACIL - 24hr",cex = 2,font = 2)
# 
# boxplot(fluo24hr78$Ind2_78_Div ~ fluo24hr78$Conc, 
#         ylim = c(0, 1.5), 
#         ylab = "Cell Viability (%)", 
#         xlab = "Concentration (uM)", 
#         main = "78-1 Div"
# )
# 
# boxplot(fluo24hr75$Ind1_75_Div ~ fluo24hr75$Conc, 
#         ylim = c(0, 1.5), 
#         ylab = "Cell Viability (%)", 
#         xlab = "Concentration (uM)", 
#         main = "75-1 Div"
# )
# 
# boxplot(fluo24hr17$Ind3_17_Div ~ fluo24hr17$Conc, 
#         ylim = c(0, 1.5), 
#         ylab = "Cell Viability (%)", 
#         xlab = "Concentration (uM)", 
#         main = "17-3 Div"
# )

```



#DOX + DMSO Final Data 48hr Boxplots
```{r Boxplots Final Data 48hr}
#####DOX Samples#####
#dox All 48HR
par(mar = c(3.0, 3.0, 1.2, 1), mgp = c(2, .7, 0))
layout(matrix(c(1, 2, 1, 3, 1, 4), nrow = 2, ncol = 3), heights = c(0.5, 2, 2, 2))
#layout.show(3)
plot.new()
text(0.5,0.5,"DOXORUBICIN - 48hr",cex = 2,font = 2)

boxplot(dox48hr78$Ind2_78_Div ~ dox48hr78$Conc, 
        ylim = c(0, 1.5), 
        ylab = "Cell Viability (%)", 
        xlab = "Concentration (uM)", 
        main = "78-1 Div"
)

boxplot(dox48hr75$Ind1_75_Div ~ dox48hr75$Conc, 
        ylim = c(0, 1.5), 
        ylab = "Cell Viability (%)", 
        xlab = "Concentration (uM)", 
        main = "75-1 Div"
)

boxplot(dox48hr17$Ind3_17_Div ~ dox48hr17$Conc, 
        ylim = c(0, 1.5), 
        ylab = "Cell Viability (%)", 
        xlab = "Concentration (uM)", 
        main = "17-3 Div"
)

#####DMSO samples#####
#DMSO All 48HR
par(mar = c(3.0, 3.0, 1.2, 1), mgp = c(2, .7, 0))
layout(matrix(c(1, 2, 1, 3, 1, 4), nrow = 2, ncol = 3), heights = c(0.5, 2, 2, 2))
#layout.show(3)
plot.new()
text(0.5,0.5,"DMSO VEHICLE - 48hr",cex = 2,font = 2)

boxplot(dmso48hr78$Ind2_78_Div ~ dmso48hr78$Conc, 
        ylim = c(0, 1.5), 
        ylab = "Cell Viability (%)", 
        xlab = "Concentration (uM)", 
        main = "78-1 Div"
)

boxplot(dmso48hr75$Ind1_75_Div ~ dmso48hr75$Conc, 
        ylim = c(0, 1.5), 
        ylab = "Cell Viability (%)", 
        xlab = "Concentration (uM)", 
        main = "75-1 Div"
)

boxplot(dmso48hr17$Ind3_17_Div ~ dmso48hr17$Conc, 
        ylim = c(0, 1.5), 
        ylab = "Cell Viability (%)", 
        xlab = "Concentration (uM)", 
        main = "17-3 Div"
)
```

```{r 5FU Boxplots Final Data 48hr, include=FALSE}
# #####FLUO samples#####
# par(mar = c(3.0, 3.0, 1.2, 1), mgp = c(2, .7, 0))
# layout(matrix(c(1, 2, 1, 3, 1, 4), nrow = 2, ncol = 3), heights = c(0.5, 2, 2, 2))
# #layout.show(3)
# plot.new()
# text(0.5,0.5,"5-FLUOROURACIL - 48hr",cex = 2,font = 2)
# 
# boxplot(fluo48hr78$Ind2_78_Div ~ fluo48hr78$Conc, 
#         ylim = c(0, 1.5), 
#         ylab = "Cell Viability (%)", 
#         xlab = "Concentration (uM)", 
#         main = "78-1 Div"
# )
# 
# boxplot(fluo48hr75$Ind1_75_Div ~ fluo48hr75$Conc, 
#         ylim = c(0, 1.5), 
#         ylab = "Cell Viability (%)", 
#         xlab = "Concentration (uM)", 
#         main = "75-1 Div"
# )
# 
# boxplot(fluo48hr17$Ind3_17_Div ~ fluo48hr17$Conc, 
#         ylim = c(0, 1.5), 
#         ylab = "Cell Viability (%)", 
#         xlab = "Concentration (uM)", 
#         main = "17-3 Div"
# )
```


#DOX + DMSO Boxplots 72hr
```{r Boxplots Final Data 72hr}
#####DOX Samples#####
#dox All 72HR
par(mar = c(3.0, 3.0, 1.2, 1), mgp = c(2, .7, 0))
layout(matrix(c(1, 2, 1, 3, 1, 4), nrow = 2, ncol = 3), heights = c(0.5, 2, 2, 2))
#layout.show(3)
plot.new()
text(0.5,0.5,"DOXORUBICIN - 72hr",cex = 2,font = 2)

boxplot(dox72hr78$Ind2_78_Div ~ dox72hr78$Conc, 
        ylim = c(0, 1.5), 
        ylab = "Cell Viability (%)", 
        xlab = "Concentration (uM)", 
        main = "78-1 Div"
)

boxplot(dox72hr75$Ind1_75_Div ~ dox72hr75$Conc, 
        ylim = c(0, 1.5), 
        ylab = "Cell Viability (%)", 
        xlab = "Concentration (uM)", 
        main = "75-1 Div"
)

boxplot(dox72hr17$Ind3_17_Div ~ dox72hr17$Conc, 
        ylim = c(0, 1.5), 
        ylab = "Cell Viability (%)", 
        xlab = "Concentration (uM)", 
        main = "17-3 Div"
)

#####DMSO samples#####
#DMSO All 72HR
par(mar = c(3.0, 3.0, 1.2, 1), mgp = c(2, .7, 0))
layout(matrix(c(1, 2, 1, 3, 1, 4), nrow = 2, ncol = 3), heights = c(0.5, 2, 2, 2))
#layout.show(3)
plot.new()
text(0.5,0.5,"DMSO VEHICLE - 72hr",cex = 2,font = 2)

boxplot(dmso72hr78$Ind2_78_Div ~ dmso72hr78$Conc, 
        ylim = c(0, 1.5), 
        ylab = "Cell Viability (%)", 
        xlab = "Concentration (uM)", 
        main = "78-1 Div"
)

boxplot(dmso72hr75$Ind1_75_Div ~ dmso72hr75$Conc, 
        ylim = c(0, 1.5), 
        ylab = "Cell Viability (%)", 
        xlab = "Concentration (uM)", 
        main = "75-1 Div"
)

boxplot(dmso72hr17$Ind3_17_Div ~ dmso72hr17$Conc, 
        ylim = c(0, 1.5), 
        ylab = "Cell Viability (%)", 
        xlab = "Concentration (uM)", 
        main = "17-3 Div"
)
```
```{r 5FU Boxplots, include=FALSE}
# #####FLUO samples#####
# par(mar = c(3.0, 3.0, 1.2, 1), mgp = c(2, .7, 0))
# layout(matrix(c(1, 2, 1, 3, 1, 4), nrow = 2, ncol = 3), heights = c(0.5, 2, 2, 2))
# #layout.show(3)
# plot.new()
# text(0.5,0.5,"5-FLUOROURACIL - 72hr",cex = 2,font = 2)
# 
# boxplot(fluo72hr78$Ind2_78_Div ~ fluo72hr78$Conc, 
#         ylim = c(0, 1.5), 
#         ylab = "Cell Viability (%)", 
#         xlab = "Concentration (uM)", 
#         main = "78-1 Div"
# )
# 
# boxplot(fluo72hr75$Ind1_75_Div ~ fluo72hr75$Conc, 
#         ylim = c(0, 1.5), 
#         ylab = "Cell Viability (%)", 
#         xlab = "Concentration (uM)", 
#         main = "75-1 Div"
# )
# 
# boxplot(fluo72hr17$Ind3_17_Div ~ fluo72hr17$Conc, 
#         ylim = c(0, 1.5), 
#         ylab = "Cell Viability (%)", 
#         xlab = "Concentration (uM)", 
#         main = "17-3 Div"
# )

```


Now that I've plotted out all of the analysis steps and nothing looks amiss, let's start fitting my models for DRC
I used the DRC package in R
At this point, I am only showing the relevant data for both treatments, as the vehicle has been divided out 
```{r Fitting Models DRCs}
#####DOX Samples#####
#24hr DOX
dox24tox_75 <- dox24hr75 %>% mutate(response = Ind1_75_Div*100)
summary(dox24tox_75$response)

dox24tox_78 <- dox24hr78 %>% mutate(response = Ind2_78_Div*100)
summary(dox24tox_78$response)

dox24tox_17 <- dox24hr17 %>% mutate(response = Ind3_17_Div*100)
summary(dox24tox_17$response)

#48hr DOX
dox48tox_75 <- dox48hr75 %>% mutate(response = Ind1_75_Div*100)
summary(dox48tox_75$response)

dox48tox_78 <- dox48hr78 %>% mutate(response = Ind2_78_Div*100)
summary(dox48tox_78$response)

dox48tox_17 <- dox48hr17 %>% mutate(response = Ind3_17_Div*100)
summary(dox48tox_17$response)

#72hr DOX
dox72tox_75 <- dox72hr75 %>% mutate(response = Ind1_75_Div*100)
summary(dox72tox_75$response)

dox72tox_78 <- dox72hr78 %>% mutate(response = Ind2_78_Div*100)
summary(dox72tox_78$response)

dox72tox_17 <- dox72hr17 %>% mutate(response = Ind3_17_Div*100)
summary(dox72tox_17$response)

```

```{r 5FU Samples Models, include=FALSE}
#####FLUO Samples#####
# #24hr FLUO
# fluo24tox_75 <- fluo24hr75 %>% mutate(response = Ind1_75_Div*100)
# summary(fluo24tox_75$response)
# 
# fluo24tox_78 <- fluo24hr78 %>% mutate(response = Ind2_78_Div*100)
# summary(fluo24tox_78$response)
# 
# fluo24tox_17 <- fluo24hr17 %>% mutate(response = Ind3_17_Div*100)
# summary(fluo24tox_17$response)
# 
# #48hr fluo
# fluo48tox_75 <- fluo48hr75 %>% mutate(response = Ind1_75_Div*100)
# summary(fluo48tox_75$response)
# 
# fluo48tox_78 <- fluo48hr78 %>% mutate(response = Ind2_78_Div*100)
# summary(fluo48tox_78$response)
# 
# fluo48tox_17 <- fluo48hr17 %>% mutate(response = Ind3_17_Div*100)
# summary(fluo48tox_17$response)
# 
# #72hr fluo
# fluo72tox_75 <- fluo72hr75 %>% mutate(response = Ind1_75_Div*100)
# summary(fluo72tox_75$response)
# 
# fluo72tox_78 <- fluo72hr78 %>% mutate(response = Ind2_78_Div*100)
# summary(fluo72tox_78$response)
# 
# fluo72tox_17 <- fluo72hr17 %>% mutate(response = Ind3_17_Div*100)
# summary(fluo72tox_17$response)
```

Now that I've fit the models and taken a look at their summary, let's plot some dose-response curves through the DRC package

I would like to have all individuals on the same plot, for each timepoint
```{r DRCs Doxorubicin All Timepoints, fig.height=6, fig.width=10, warning=FALSE}

par(mar = c(3.0, 3.0, 1.2, 1), mgp = c(2, .7, 0))
layout(matrix(c(1, 2, 1, 3, 1, 4), nrow = 2, ncol = 3), heights = c(0.3, 1, 1, 1))
#layout.show(3)
plot.new()
text(0.5,0.5,"DOXORUBICIN RECOVERY CONCENTRATION-RESPONSE",cex = 2,font = 2)
#24hr plots
doxtox24_78_model <- drm(response~Conc, data = dox24tox_78, fct = LL.4(fixed = c(NA, 0, 100, NA)))
plot(doxtox24_78_model, type = "none", broken = TRUE, 
     xt = c(0.01, 0.1, 0.5, 1, 5, 10, 50, 100, 1000), xttrim = FALSE,  
     ylim = c(0,110), cex = 1, col = "#9ACCDE", lwd = 4, ylab = "Percent Viability (%)",
     xlab = "Concentration (uM)", main = "24HR FOLLOWING TREATMENT", lty = c(1),
     xaxs = "i", yaxs = "i")

par(new=TRUE)
doxtox24_75_model <- drm(response~Conc, data = dox24tox_75, fct = LL.4(fixed = c(NA, 0, 100, NA)))
plot(doxtox24_75_model, add = TRUE, col = "#499FBD", lwd = 4, lty = c(1), type = "none")

par(new=TRUE)
doxtox24_17_model <- drm(response~Conc, data = dox24tox_17, fct = LL.4(fixed = c(NA, 0, 100, NA)))
plot(doxtox24_17_model, add = TRUE, col = "#254F5E", lwd = 4, lty = c(1), type = "none")

par(new=TRUE)
legend(x = "bottomleft", legend = c("78-1", "75-1", "17-3"), lty = c(1, 1, 1, 1), col = c("#9ACCDE", "#499FBD", "#254F5E"), lwd = 4, cex = 1, title = "iPSC-CM Lines")

#48hr plots
doxtox48_78_model <- drm(response~Conc, data = dox48tox_78, fct = LL.4(fixed = c(NA, NA, 100, NA)))
plot(doxtox48_78_model, type = "none", broken = TRUE, 
     xt = c(0.01, 0.1, 0.5, 1, 5, 10, 50, 100, 1000), xttrim = FALSE,  
     ylim = c(0,110), cex = 1, col = "#9ACCDE", lwd = 4, ylab = "Percent Viability (%)", xlab = "Concentration (uM)", main = "48HR FOLLOWING TREATMENT", lty = c(2),
     xaxs = "i", yaxs = "i")

par(new=TRUE)
doxtox48_75_model <- drm(response~Conc, data = dox48tox_75, fct = LL.4(fixed = c(NA, NA, NA, NA)))
plot(doxtox48_75_model, add = TRUE, col = "#499FBD", lwd = 4, lty = c(2), type = "none")

par(new=TRUE)
doxtox48_17_model <- drm(response~Conc, data = dox48tox_17, fct = LL.4(fixed = c(NA, 0, 100, NA)))
plot(doxtox48_17_model, add = TRUE, col = "#254F5E", lwd = 4, lty = c(2), type = "none")

#72hr plots
doxtox72_78_model <- drm(response~Conc, data = dox72tox_78, fct = LL.4(fixed = c(NA, NA, 100, NA)))
plot(doxtox72_78_model, type = "none", broken = TRUE, 
     xt = c(0.01, 0.1, 0.5, 1, 5, 10, 50, 100, 1000), xttrim = FALSE,  
     ylim = c(0, 110), cex = 1, col = "#9ACCDE", lwd = 4, ylab = "Percent Viability (%)",
     xlab = "Concentration (uM)", main = "72HR FOLLOWING TREATMENT", lty = c(3), 
     xaxs = "i", yaxs = "i")

par(new=TRUE)
doxtox72_75_model <- drm(response~Conc, data = dox72tox_75, fct = LL.4(fixed = c(NA, 0, 100, NA)))
plot(doxtox72_75_model, add = TRUE, col = "#499FBD", lwd = 4, lty = c(3), type = "none")

par(new=TRUE)
doxtox72_17_model <- drm(response~Conc, data = dox72tox_17, fct = LL.4(fixed = c(NA, 0, 100, NA)))
plot(doxtox72_17_model, add = TRUE, col = "#254F5E", lwd = 4, lty = c(3), type = "none")


```

```{r DRCs 5-Fluorouracil All Timepoints, fig.width=10, fig.height=6, warning=FALSE, include=FALSE}

# par(mar = c(3.0, 3.0, 1.2, 1), mgp = c(2, .7, 0))
# layout(matrix(c(1, 2, 1, 3, 1, 4), nrow = 2, ncol = 3), heights = c(0.3, 1, 1, 1))
# #layout.show(3)
# plot.new()
# text(0.5,0.5,"5-FLUOROURACIL RECOVERY CONCENTRATION-RESPONSE",cex = 2,font = 2)
# #24hr plots
# fluotox24_75_model <- drm(response~Conc, data = fluo24tox_75, fct = LL.4(fixed = c(NA, NA, NA, NA)))
# plot(fluotox24_75_model, type = "none", broken = TRUE, 
#      xt = c(0.01, 0.1, 1, 5, 10, 50, 100, 1000, 10000), xttrim = FALSE,  
#      ylim = c(0,110), cex = 1, col = "#DCACED", lwd = 4, ylab = "Percent Viability (%)",
#      xlab = "Concentration (uM)", main = "24HR FOLLOWING TREATMENT", lty = c(1),
#      xaxs = "i", yaxs = "i")
# 
# par(new=TRUE)
# fluotox24_78_model <- drm(response~Conc, data = fluo24tox_78, fct = LL.4(fixed = c(NA, 0, 100, NA)))
# plot(fluotox24_78_model, add = TRUE, col = "#674C71", lwd = 4, lty = c(1), type = "none")
# 
# par(new=TRUE)
# fluotox24_17_model <- drm(response~Conc, data = fluo24tox_17, fct = LL.4(fixed = c(NA, NA, NA, NA)))
# plot(fluotox24_17_model, add = TRUE, col = "#EACDF4", lwd = 4, lty = c(1), type = "none")
# 
# par(new=TRUE)
# legend(x = "bottomleft", legend = c("75-1", "78-1", "17-3"), lty = c(1, 1, 1, 1), col = c("#DCACED", "#674C71", "#EACDF4"), lwd = 4, cex = 1, title = "iPSC-CM Lines")
# 
# #48hr plots
# fluotox48_75_model <- drm(response~Conc, data = fluo48tox_75, fct = LL.4(fixed = c(NA, NA, NA, NA)))
# plot(fluotox48_75_model, type = "none", broken = TRUE, 
#      xt = c(0.01, 0.1, 1, 5, 10, 50, 100, 1000, 10000), xttrim = FALSE,  
#      ylim = c(0,110), cex = 1, col = "#DCACED", lwd = 4, ylab = "Percent Viability (%)", xlab = "Concentration (uM)", main = "48HR FOLLOWING TREATMENT", lty = c(2),
#      xaxs = "i", yaxs = "i")
# 
# par(new=TRUE)
# fluotox48_78_model <- drm(response~Conc, data = fluo48tox_78, fct = LL.4(fixed = c(NA, NA, NA, NA)))
# plot(fluotox48_78_model, add = TRUE, col = "#674C71", lwd = 4, lty = c(2), type = "none")
# 
# par(new=TRUE)
# fluotox48_17_model <- drm(response~Conc, data = fluo48tox_17, fct = LL.4(fixed = c(NA, NA, 100, NA)))
# plot(fluotox48_17_model, add = TRUE, col = "#EACDF4", lwd = 4, lty = c(2), type = "none")
# 
# #72hr plots
# fluotox72_75_model <- drm(response~Conc, data = fluo72tox_75, fct = LL.4(fixed = c(NA, NA, 100, NA)))
# plot(fluotox72_75_model, type = "none", broken = TRUE, 
#      xt = c(0.01, 0.1, 1, 5, 10, 50, 100, 1000, 10000), xttrim = FALSE,  
#      ylim = c(0, 110), cex = 1, col = "#DCACED", lwd = 4, ylab = "Percent Viability (%)",
#      xlab = "Concentration (uM)", main = "72HR FOLLOWING TREATMENT", lty = c(3), 
#      xaxs = "i", yaxs = "i")
# 
# par(new=TRUE)
# fluotox72_78_model <- drm(response~Conc, data = fluo72tox_78, fct = LL.4(fixed = c(NA, NA, 100, NA)))
# plot(fluotox72_78_model, add = TRUE, col = "#674C71", lwd = 4, lty = c(3), type = "none")
# 
# par(new=TRUE)
# fluotox72_17_model <- drm(response~Conc, data = fluo72tox_17, fct = LL.4(fixed = c(NA, NA, NA, NA)))
# plot(fluotox72_17_model, add = TRUE, col = "#EACDF4", lwd = 4, lty = c(3), type = "none")

```



Test to see if I can plot all of these on the same plot using colors and lines
```{r DRCs All Timepoints, fig.width=12, fig.height=8, warning=FALSE}
#for this to work I need to find unique lines/colors for all of these 
#this will include 5-Fluorouracil and Doxorubicin

par(mar = c(3.0, 3.0, 1.2, 1), mgp = c(2, .7, 0))
layout(matrix(c(1, 2, 1, 3), nrow = 2, ncol = 2), heights = c(0.4, 2, 2, 2))
#layout.show(3)
plot.new()
text(0.5,0.5,"RECOVERY CONCENTRATION-RESPONSE",cex = 2,font = 2)
#24hr plots
doxtox24_75_model <- drm(response~Conc, data = dox24tox_75, fct = LL.4(fixed = c(NA, 0, 100, NA)))
plot(doxtox24_75_model, type = "none", broken = TRUE, 
     xt = c(0.01, 0.1, 0.5, 1, 5, 10, 50, 100, 1000), xttrim = FALSE,  
     ylim = c(0,110), cex = 1, col = "#9ACCDE", lwd = 4, ylab = "Percent Viability (%)",
     xlab = "Concentration (uM)", main = "24HR FOLLOWING TREATMENT", lty = c(1),
     xaxs = "i", yaxs = "i")

par(new=TRUE)
doxtox24_78_model <- drm(response~Conc, data = dox24tox_78, fct = LL.4(fixed = c(NA, 0, 100, NA)))
plot(doxtox24_78_model, add = TRUE, col = "#499FBD", lwd = 4, lty = c(1), type = "none")

par(new=TRUE)
doxtox24_17_model <- drm(response~Conc, data = dox24tox_17, fct = LL.4(fixed = c(NA, 0, 100, NA)))
plot(doxtox24_17_model, add = TRUE, col = "#254F5E", lwd = 4, lty = c(1), type = "none")

#48hr plots
par(new=TRUE)
doxtox48_75_model <- drm(response~Conc, data = dox48tox_75, fct = LL.4(fixed = c(NA, NA, 100, NA)))
plot(doxtox48_75_model, add = TRUE, col = "#9ACCDE", lwd = 4, lty = c(2), type = "none")

par(new=TRUE)
doxtox48_78_model <- drm(response~Conc, data = dox48tox_78, fct = LL.4(fixed = c(NA, NA, 100, NA)))
plot(doxtox48_78_model, add = TRUE, col = "#499FBD", lwd = 4, lty = c(2), type = "none")

par(new=TRUE)
doxtox48_17_model <- drm(response~Conc, data = dox48tox_17, fct = LL.4(fixed = c(NA, 0, 100, NA)))
plot(doxtox48_17_model, add = TRUE, col = "#254F5E", lwd = 4, lty = c(2), type = "none")

#72hr plots
par(new=TRUE)
doxtox72_75_model <- drm(response~Conc, data = dox72tox_75, fct = LL.4(fixed = c(NA, NA, 100, NA)))
plot(doxtox72_75_model, add = TRUE, col = "#9ACCDE", lwd = 4, lty = c(3), type = "none")

par(new=TRUE)
doxtox72_78_model <- drm(response~Conc, data = dox72tox_78, fct = LL.4(fixed = c(NA, 0, 100, NA)))
plot(doxtox72_78_model, add = TRUE, col = "#499FBD", lwd = 4, lty = c(3), type = "none")

par(new=TRUE)
doxtox72_17_model <- drm(response~Conc, data = dox72tox_17, fct = LL.4(fixed = c(NA, 0, 100, NA)))
plot(doxtox72_17_model, add = TRUE, col = "#254F5E", lwd = 4, lty = c(3), type = "none")

par(new=TRUE)
legend(x = "bottomleft", legend = c("Ind1 24hr", "Ind2 24hr", "Ind3 24hr", "Ind1 48hr", "Ind2 48hr", "Ind3 48hr", "Ind1 72hr", "Ind2 72hr", "Ind3 72hr"), lty = c(1, 1, 1, 2, 2, 2, 3, 3, 3, 1), col = rep(c("#9ACCDE", "#499FBD", "#254F5E"),3), lwd = 4, cex = 1)

#now add the fluo plots
#24hr plots
fluotox24_75_model <- drm(response~Conc, data = fluo24tox_75, fct = LL.4(fixed = c(NA, NA, NA, NA)))
plot(fluotox24_75_model, type = "none", broken = TRUE, 
     xt = c(0.01, 0.1, 1, 5, 10, 50, 100, 1000, 10000), xttrim = FALSE,  
     ylim = c(0,110), cex = 1, col = "#DCACED", lwd = 4, ylab = "Percent Viability (%)",
     xlab = "Concentration (uM)", main = "5-FLUOROURACIL TREATMENT", lty = c(1),
     xaxs = "i", yaxs = "i")

par(new=TRUE)
fluotox24_78_model <- drm(response~Conc, data = fluo24tox_78, fct = LL.4(fixed = c(NA, 0, 100, NA)))
plot(fluotox24_78_model, add = TRUE, col = "#9B72AA", lwd = 4, lty = c(1), type = "none")

par(new=TRUE)
fluotox24_17_model <- drm(response~Conc, data = fluo24tox_17, fct = LL.4(fixed = c(NA, NA, NA, NA)))
plot(fluotox24_17_model, add = TRUE, col = "#674C71", lwd = 4, lty = c(1), type = "none")

#48hr plots
par(new=TRUE)
fluotox48_75_model <- drm(response~Conc, data = fluo48tox_75, fct = LL.4(fixed = c(NA, NA, NA, NA)))
plot(fluotox48_75_model, add = TRUE, col = "#DCACED", lwd = 4, lty = c(2), type = "none")

par(new=TRUE)
fluotox48_78_model <- drm(response~Conc, data = fluo48tox_78, fct = LL.4(fixed = c(NA, NA, NA, NA)))
plot(fluotox48_78_model, add = TRUE, col = "#9B72AA", lwd = 4, lty = c(2), type = "none")

par(new=TRUE)
fluotox48_17_model <- drm(response~Conc, data = fluo48tox_17, fct = LL.4(fixed = c(NA, NA, 100, NA)))
plot(fluotox48_17_model, add = TRUE, col = "#674C71", lwd = 4, lty = c(2), type = "none")

#72hr plots
par(new=TRUE)
fluotox72_78_model <- drm(response~Conc, data = fluo72tox_78, fct = LL.4(fixed = c(NA, NA, 100, NA)))
plot(fluotox72_75_model, add = TRUE, col = "#DCACED", lwd = 4, lty = c(3), type = "none")

par(new=TRUE)
fluotox72_78_model <- drm(response~Conc, data = fluo72tox_78, fct = LL.4(fixed = c(NA, NA, 100, NA)))
plot(fluotox72_78_model, add = TRUE, col = "#9B72AA", lwd = 4, lty = c(3), type = "none")

par(new=TRUE)
fluotox72_17_model <- drm(response~Conc, data = fluo72tox_17, fct = LL.4(fixed = c(NA, NA, NA, NA)))
plot(fluotox72_17_model, add = TRUE, col = "#674C71", lwd = 4, lty = c(3), type = "none")

legend(x = "bottomleft", legend = c("Ind1 24hr", "Ind2 24hr", "Ind3 24hr", "Ind1 48hr", "Ind2 48hr", "Ind3 48hr", "Ind1 72hr", "Ind2 72hr", "Ind3 72hr"), lty = c(1, 1, 1, 2, 2, 2, 3, 3, 3, 1), col = rep(c("#DCACED", "#9B72AA", "#674C71"),3), lwd = 4)


#had to change the legends to show all of the line types and colors
#24hr = line 1, 48hr = line 2, 72hr = line 3

```

```{r 24hr Only for Figure 1}
#I want to make a small plot that only contains 24hr and calculates an average LD50 for all three cell lines
#I also want to place a grey line on the graph where my concentration is
par(mar = c(3.0, 3.0, 1.2, 1), mgp = c(2, .7, 0))
layout(matrix(c(1, 2, 1, 3, 1, 4), nrow = 2, ncol = 3), heights = c(0.3, 1, 1, 1))
#layout.show(3)
plot.new()
text(0.5,0.5,"DOXORUBICIN RECOVERY CONCENTRATION-RESPONSE",cex = 2,font = 2)
#24hr plots
doxtox24_75_model <- drm(response~Conc, data = dox24tox_75, fct = LL.4(fixed = c(NA, 0, 100, NA)))
plot(doxtox24_75_model, type = "none", broken = TRUE, 
     xt = c(0.01, 0.1, 0.5, 1, 5, 10, 50, 100, 1000), xttrim = FALSE,  
     ylim = c(0,110), cex = 1, col = "#9ACCDE", lwd = 4, ylab = "Percent Viability (%)",
     xlab = "Concentration (uM)", main = "24HR FOLLOWING TREATMENT", lty = c(1),
     xaxs = "i", yaxs = "i")

par(new=TRUE)
doxtox24_78_model <- drm(response~Conc, data = dox24tox_78, fct = LL.4(fixed = c(NA, 0, 100, NA)))
plot(doxtox24_78_model, add = TRUE, col = "#499FBD", lwd = 4, lty = c(1), type = "none")

par(new=TRUE)
doxtox24_17_model <- drm(response~Conc, data = dox24tox_17, fct = LL.4(fixed = c(NA, 0, 100, NA)))
plot(doxtox24_17_model, add = TRUE, col = "#254F5E", lwd = 4, lty = c(1), type = "none")

par(new=TRUE)
legend(x = "bottomleft", legend = c("75-1", "78-1", "17-3"), lty = c(1, 1, 1, 1), col = c("#9ACCDE", "#499FBD", "#254F5E"), lwd = 4, cex = 1, title = "iPSC-CM Lines")

```


```{r 24hr Only w LD50 and conc line}

conc_labels <- c(0.01, 0.1, 0.5, 1, 10, 50, 100, 1000)
pct_labels <- c(0, 10, 20, 30, 40, 50, 60, 70, 80, 90, 100)

# Fit models
doxtox24_78_model <- drm(response ~ Conc, data = dox24tox_78, fct = LL.4(fixed = c(NA, 0, 100, NA)))
doxtox24_75_model <- drm(response ~ Conc, data = dox24tox_75, fct = LL.4(fixed = c(NA, 0, 100, NA)))
doxtox24_17_model <- drm(response ~ Conc, data = dox24tox_17, fct = LL.4(fixed = c(NA, 0, 100, NA)))

# Extract LD50 (ED50)
ed75 <- ED(doxtox24_78_model, 50, interval = "delta")[1]
ed78 <- ED(doxtox24_75_model, 50, interval = "delta")[1]
ed17 <- ED(doxtox24_17_model, 50, interval = "delta")[1]

avg_ld50 <- mean(c(ed78, ed75, ed17))

# Plot first model, then overlay
plot(doxtox24_78_model, type = "none", broken = TRUE,
     ylim = c(0,100), col = "#9ACCDE", lwd = 3,
     ylab = "Percent Viability (%)", xlab = "Concentration (uM)",
     main = "24hr Treatment", log = "x", axes = FALSE)

plot(doxtox24_75_model, add = TRUE, col = "#499FBD", lwd = 3, type = "none")
plot(doxtox24_17_model, add = TRUE, col = "#254F5E", lwd = 3, type = "none")

axis(1, at = conc_labels, labels = conc_labels, las = 2, cex.axis = 0.8)

axis(2, at = pct_labels, labels = pct_labels, las = 2, cex.axis = 0.7)

# Grey vertical reference line (example at 0.5 uM)
abline(v = 0.5, col = "grey50", lty = 2, lwd = 2)
# text(x = 0.5, y = 99, 
#      labels = "0.5 M", 
#      col = "grey30", pos = 4, cex = 0.8, font = 2)

# LD50 vertical lines for each line
# abline(v = ed78, col = "#9ACCDE", lty = 2, lwd = 2)
# abline(v = ed75, col = "#499FBD", lty = 2, lwd = 2)
# abline(v = ed17, col = "#254F5E", lty = 2, lwd = 2)

# Average LD50 line in red
abline(v = avg_ld50, col = "red", lty = 3, lwd = 2)
text(x = avg_ld50, y = 99,        # y=105 puts it just above top of plot
     labels = paste0("Avg LD50 = ", round(avg_ld50, 2), " M"),
     col = "red", pos = 4, cex = 0.8, font = 2)

# Legend
# legend("bottomleft",
#        legend = c(
#          paste0("Ind3"),
#          paste0("Ind4"),
#          paste0("Ind5"),
#          paste0("Avg LD50 = ", round(avg_ld50, 2), " M")
#        ),
#        col = c("#9ACCDE", "#499FBD", "#254F5E", "red"),
#        lwd = 3, lty = c(1,1,1,3), cex = 0.8,
#        title = "Individuals")

# Legend
legend("bottomleft",
       legend = c(
         paste0("Ind3 (LD50 =", round(ed78, 2), " M)"),
         paste0("Ind4 (LD50 =", round(ed75, 2), " M)"),
         paste0("Ind5 (LD50 =", round(ed17, 2), " M)")
         # paste0("Avg LD50 =", round(avg_ld50, 2), " M")
       ),
       col = c("#9ACCDE", "#499FBD", "#254F5E"),
       lwd = 3, lty = c(1,1,1,3), cex = 0.8,
       title = "Individuals")


```


```{r 24hr only Separate Legend}
par(mar = c(4, 4, 2, 2), oma = c(0, 0, 0, 0))
layout(matrix(c(1,2), nrow=2), heights = c(4, 2))

#I swapped 78-1 and 75-1 for this so I could have the individual numbers in order (Ind3, 4, 5)
# Plot in first (big) panel
plot(doxtox24_78_model, type = "none", broken = TRUE,
     ylim = c(0, 100), col = "#9ACCDE", lwd = 3,
     ylab = "Percent Viability (%)", xlab = "Concentration (uM)",
     main = "24hr Treatment", log = "x",
     axes = FALSE)
plot(doxtox24_75_model, add = TRUE, col = "#499FBD", lwd = 3, type = "none")
plot(doxtox24_17_model, add = TRUE, col = "#254F5E", lwd = 3, type = "none")
axis(2, at = pct_labels, labels = pct_labels, las = 2)
axis(1, at = conc_labels, labels = conc_labels, las = 2)
box()
#line for conc 0.5
abline(v = 0.5, col = "grey50", lty = 2, lwd = 2)
#line for avg ld50
abline(v = avg_ld50, col = "red", lty = 3, lwd = 2)

# Empty plot for legend
plot.new()
legend("center",
       legend = c(
         paste0("Ind3 (LD50 =", round(ed75, 2), " M)"),
         paste0("Ind4 (LD50 =", round(ed78, 2), " M)"),
         paste0("Ind5 (LD50 =", round(ed17, 2), " M)"),
         paste0("Avg LD50 =", round(avg_ld50, 2), " M")
       ),
       col = c("#9ACCDE", "#499FBD", "#254F5E", "red"),
       lwd = 3, lty = c(1,1,1,3),
       cex = 0.7,
       horiz = FALSE,
       bty = "o")

```

